### 2024-02-21 paper/paper.tex
add template information

\documentclass[sigconf]{acmart}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\usepackage{etoolbox} 
\apptocmd{\sloppy}{\hbadness 10000\relax} {}{}

\usepackage[skip=6pt plus1pt]{parskip} %% add space between the paragraphs

\usepackage{graphicx} %% For pictures
\usepackage[section]{placeins} %% used to keep the images in the section that I want them in

\begin{document}

\title{Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency}

\author{Jonquill Howlett}
\affiliation{%
  \institution{Colorado State University}
  \city{Berthoud}
  \state{Colorado}
  \country{USA}
  \postcode{80513-0650} %chktex 8
}
\email{jonquill.howlett@colostate.edu}

\author{Lianna Hoag}
\affiliation{%
  \institution{Colorado State University}
  \city{Fort Collins}
  \state{Colorado}
  \country{USA}
  \postcode{80525-0650} %chktex 8 %the rest of the zip will need to be corrected
}
\email{jonquill.howlett@colostate.edu} %update email

\author{Shea Spalding}
\affiliation{%
  \institution{Colorado State University}
  \city{Fort Collins}
  \state{Colorado}
  \country{USA}
  \postcode{80525-0650} %chktex 8 %the rest of the zip will need to be corrected
}
\email{jonquill.howlett@colostate.edu} %update email

\renewcommand{\shortauthors}{J. Howlett} %I don't know how to format this for three authors

\begin{abstract}
abstract
\end{abstract}

\ccsdesc{Music, Typing Efficiency} %May not need this
\keywords{Typing Efficiency with Music, Cognitive Function} % placeholder text for the time being
\maketitle

\section*{Introduction}
Introduction

\section*{Methodoloy}
methods

test\cite{AudioDistractionsAshley}

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

\end{document}

### 2024-02-22 paper/paper.tex
changed headings to be numerical
Update paper.tex

@@
   \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
+    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}} %chktex 1
 
 \usepackage{etoolbox} 
-\apptocmd{\sloppy}{\hbadness 10000\relax} {}{}
+\apptocmd{\sloppy}{\hbadness 10000\relax} {}{} %chktex 1
 
@@
 
-\section*{Introduction}
+\section{Introduction}
 Introduction
+This project will focus on people’s ability to type with distractions such as different types of music playing and then will test their cognitive ability to focus on a hand/eye coordination test in which we will test how well they can match shapes by measuring speed and accuracy.
+The purpose of the two-part test is to help test if the music is too much of a distraction or will help the people be more efficient at their work.
+This is important because many people do their homework or jobs while listening to music and should they make a mistake, it could end up costing someone their grade or the mistake at work has a cascading effect to cause more errors in their work.
+The two-part test will help determine if there is a correlation between the effectiveness of music versus no music on cognitive response time and typing efficiency.
 
-\section*{Methodoloy}
+\section{Methodoloy}
 methods

### 2024-02-26 typingTest/type.py
small set for word bank

@@ -1,0 +1,22 @@
+from time import time
+import random
+
+def wordBank():
+    one = "typingTest/lovestory"
+    two = "typingTest/dontstopbelievin"
+    three = "typingTest/yesterday"
+    four = "typingTest/beforehecheats"
+    five = "typingTest/hundredyears"
+
+    choices = [one, two, three, four, five]
+    word = random.choice(choices)
+    return word
+
+def main():
+    filename = wordBank()
+    with open(filename, 'r') as file:
+        original = file.read()
+    print(original)
+
+if __name__ == '__main__':    
+    main()

### 2024-02-27 paper/paper.tex

@@
 \section{Introduction}
-Introduction
-This project will focus on people’s ability to type with distractions such as different types of music playing and then will test their cognitive ability to focus on a hand/eye coordination test in which we will test how well they can match shapes by measuring speed and accuracy.
+This project will focus on people's ability to type with distractions such as different types of music playing and then will test their cognitive ability to focus on a hand/eye coordination test in which we will test how well they can match shapes by measuring speed and accuracy.
 The purpose of the two-part test is to help test if the music is too much of a distraction or will help the people be more efficient at their work. 
@@
 methods
+test\cite{AudioDistractionsAshley}
 
-test\cite{AudioDistractionsAshley}
+\subsection[short]{Participants}
+Participants
+
+\subsection[short]{Apparatus}
+Apparatus
+
+\subsection[short]{Procedure}
+Procedure
+
+\subsection[short]{Design}
+Design
+
+\section{Results and Discussion}
+Results and Discussion
+
+\section{Conclusion}
+Conclusion
 

### 2024-03-08 paper/paper.tex

@@
 
-\ccsdesc{Music, Typing Efficiency} %May not need this
+\ccsdesc{Music, Typing Efficiency} % Update this
 \keywords{Typing Efficiency with Music, Cognitive Function} % placeholder text for the time being
@@
 
-\section{Methodoloy}
-methods
-test\cite{AudioDistractionsAshley}
+\section{Methodology}
+After going through all the consent forms, the user will take the typing test. It will pull lyrics from popular songs and display in a graphical user interface (GUI). 
+The interface will calculate the speed and accuracy in the backend of the program with the user just having to take the test. They will take the test (NUMBER OF LEVELS OF MUSIC)
+while they take the test with music and no music. They will then move on the the QBTest?. % This will need to be re-written.
+
+This is a placeholder for a citation cos otherwise the compiler throws errors \cite{AudioDistractionsAshley}.
 

### 2024-03-10 typingTest/type.py
saving spot

@@ -1,12 +1,24 @@
 from time import time
 import random
+import tkinter as tk
+
+def gui():
+    # check for tkinter version
+    # print(tk._test())
+    print(tk.Tcl().eval('info patchlevel'))
+
 
 def wordBank():
-    one = "typingTest/lovestory"
-    two = "typingTest/dontstopbelievin"
-    three = "typingTest/yesterday"
-    four = "typingTest/beforehecheats"
-    five = "typingTest/hundredyears"
+    # one = "typingTest/lovestory"
+    # two = "typingTest/dontstopbelievin"
+    # three = "typingTest/yesterday"
+    # four = "typingTest/beforehecheats"
+    # five = "typingTest/hundredyears"
+    one = "lovestory"
+    two = "dontstopbelievin"
+    three = "yesterday"
+    four = "beforehecheats"
+    five = "hundredyears"
 
     choices = [one, two, three, four, five]
     word = random.choice(choices)

### 2024-03-10 typingTest/type.py
add window

@@ -3,9 +3,19 @@ import random
 import tkinter as tk
 
 def gui():
-    # check for tkinter version
-    # print(tk._test())
-    print(tk.Tcl().eval('info patchlevel'))
+    # print(tk.Tcl().eval('info patchlevel'))     # check for tkinter version
+    window = tk.Tk() # instance of new window
+    window.geometry("800x600") # Horizontal x Vertical
+    window.minsize(800, 600)
+    window.maxsize(1000, 800)
+
+    header = tk.Label(text = "hello world") # label for the window display purposes only
+    header.pack() # add the label to the window
+
+    button = tk.Button(window, text = "Start the Game", command= window.destroy) # atm window.destroy closes the window
+    button.pack(side = "bottom", padx=10, pady=5)
+
+    window.mainloop() # display the window and label
 
 
 def wordBank():
@@ -25,6 +35,7 @@ def wordBank():
     return word
 
 def main():
+    gui()
     filename = wordBank()
     with open(filename, 'r') as file:
         original = file.read()

### 2024-03-10 typingTest/type.py
prints to gui

@@ -2,22 +2,6 @@ from time import time
 import random
 import tkinter as tk
 
-def gui():
-    # print(tk.Tcl().eval('info patchlevel'))     # check for tkinter version
-    window = tk.Tk() # instance of new window
-    window.geometry("800x600") # Horizontal x Vertical
-    window.minsize(800, 600)
-    window.maxsize(1000, 800)
-
-    header = tk.Label(text = "hello world") # label for the window display purposes only
-    header.pack() # add the label to the window
-
-    button = tk.Button(window, text = "Start the Game", command= window.destroy) # atm window.destroy closes the window
-    button.pack(side = "bottom", padx=10, pady=5)
-
-    window.mainloop() # display the window and label
-
-
 def wordBank():
     # one = "typingTest/lovestory"
     # two = "typingTest/dontstopbelievin"
@@ -34,12 +18,37 @@ def wordBank():
     word = random.choice(choices)
     return word
 
+    
+def gui():
+    # print(tk.Tcl().eval('info patchlevel'))     # check for tkinter version
+    window = tk.Tk() # instance of new window
+    window.geometry("800x600") # Horizontal x Vertical
+    window.minsize(800, 600)
+    window.maxsize(1000, 800)
+
+    def test():
+        button.destroy()
+        filename = wordBank()
+        # print(filename)
+        with open(filename, 'r') as file:
+            original = file.read()
+        label = tk.Label(window, text=original)
+        label.pack()
+
+    header = tk.Label(text = "Typing Test") # label for the window display purposes only
+    header.pack() # add the label to the window
+
+    button = tk.Button(window, text = "Start the Game", command=test) # atm window.destroy closes the window
+    button.pack(side = "bottom", padx=10, pady=5)
+
+    window.mainloop() # display the window and label
+
 def main():
     gui()
-    filename = wordBank()
-    with open(filename, 'r') as file:
-        original = file.read()
-    print(original)
+    # filename = wordBank()
+    # with open(filename, 'r') as file:
+    #     original = file.read()
+    # print(original)
 
 if __name__ == '__main__':    
     main()

### 2024-03-10 typingTest/type.py
need to change to a class

@@ -18,7 +18,6 @@ def wordBank():
     word = random.choice(choices)
     return word
 
-    
 def gui():
     # print(tk.Tcl().eval('info patchlevel'))     # check for tkinter version
     window = tk.Tk() # instance of new window
@@ -26,8 +25,8 @@ def gui():
     window.minsize(800, 600)
     window.maxsize(1000, 800)
 
-    def test():
-        button.destroy()
+    def test(): # function needs to be in the gui 
+        button.destroy() # destroys the button that says "start the game"
         filename = wordBank()
         # print(filename)
         with open(filename, 'r') as file:
@@ -35,20 +34,16 @@ def gui():
         label = tk.Label(window, text=original)
         label.pack()
 
-    header = tk.Label(text = "Typing Test") # label for the window display purposes only
+    header = tk.Label(text = "Typing Test") # label for the window - display purposes only
     header.pack() # add the label to the window
 
-    button = tk.Button(window, text = "Start the Game", command=test) # atm window.destroy closes the window
+    button = tk.Button(window, text = "Start the Game", command=test)
     button.pack(side = "bottom", padx=10, pady=5)
 
     window.mainloop() # display the window and label
 
 def main():
     gui()
-    # filename = wordBank()
-    # with open(filename, 'r') as file:
-    #     original = file.read()
-    # print(original)
 
 if __name__ == '__main__':    
     main()

### 2024-03-10 typingTest/class.py
switch to class

@@ -1,0 +1,49 @@
+from time import time
+import random
+import tkinter as tk
+
+def wordBank():
+    # one = "typingTest/lovestory"
+    # two = "typingTest/dontstopbelievin"
+    # three = "typingTest/yesterday"
+    # four = "typingTest/beforehecheats"
+    # five = "typingTest/hundredyears"
+    one = "lovestory"
+    two = "dontstopbelievin"
+    three = "yesterday"
+    four = "beforehecheats"
+    five = "hundredyears"
+
+    choices = [one, two, three, four, five]
+    word = random.choice(choices)
+    return word
+
+class gui(tk.Tk):
+    def __init__(self):
+        super().__init__()
+
+        self.geometry("800x600") # Horizontal x Vertical
+        self.minsize(800, 600)
+        self.maxsize(1000, 800)
+
+        header = tk.Label(text = "Typing Test") # label for the window - display purposes only
+        header.pack() # add the label to the window
+
+        start = tk.Button(self, text = "Start the Game", command=self.getFile) # need to change test to function to call filename
+        start.pack(side = "bottom", padx=10, pady=5)
+
+    def getFile(self):
+        # tk.Button.destroy(self) # destroys the button that says "start the game"
+        filename = wordBank()
+        # print(filename)
+        with open(filename, 'r') as file:
+            original = file.read()
+        label = tk.Label(self, text=original)
+        label.pack()
+
+def main():
+    one = gui()
+    one.mainloop()
+
+if __name__ == '__main__':    
+    main()

### 2024-03-10 typingTest/class.py
same functionality as type.py

@@ -26,20 +26,20 @@ class gui(tk.Tk):
         self.minsize(800, 600)
         self.maxsize(1000, 800)
 
-        header = tk.Label(text = "Typing Test") # label for the window - display purposes only
-        header.pack() # add the label to the window
+        self.header = tk.Label(text = "Typing Test") # label for the window - display purposes only
+        self.header.pack() # add the label to the window
 
-        start = tk.Button(self, text = "Start the Game", command=self.getFile) # need to change test to function to call filename
-        start.pack(side = "bottom", padx=10, pady=5)
+        self.start = tk.Button(self, text = "Start the Game", command=self.getFile) # need to change test to function to call filename
+        self.start.pack(side = "bottom", padx=10, pady=5)
 
     def getFile(self):
-        # tk.Button.destroy(self) # destroys the button that says "start the game"
         filename = wordBank()
         # print(filename)
         with open(filename, 'r') as file:
             original = file.read()
         label = tk.Label(self, text=original)
         label.pack()
+        self.start.destroy()
 
 def main():
     one = gui()

### 2024-03-11 typingTest/class.py
swap word bank to class

@@ -2,21 +2,21 @@ from time import time
 import random
 import tkinter as tk
 
-def wordBank():
-    # one = "typingTest/lovestory"
-    # two = "typingTest/dontstopbelievin"
-    # three = "typingTest/yesterday"
-    # four = "typingTest/beforehecheats"
-    # five = "typingTest/hundredyears"
-    one = "lovestory"
-    two = "dontstopbelievin"
-    three = "yesterday"
-    four = "beforehecheats"
-    five = "hundredyears"
+# def wordBank():
+#     # one = "typingTest/lovestory"
+#     # two = "typingTest/dontstopbelievin"
+#     # three = "typingTest/yesterday"
+#     # four = "typingTest/beforehecheats"
+#     # five = "typingTest/hundredyears"
+#     one = "lovestory"
+#     two = "dontstopbelievin"
+#     three = "yesterday"
+#     four = "beforehecheats"
+#     five = "hundredyears"
 
-    choices = [one, two, three, four, five]
-    word = random.choice(choices)
-    return word
+#     choices = [one, two, three, four, five]
+#     word = random.choice(choices)
+#     return word
 
 class gui(tk.Tk):
     def __init__(self):
@@ -32,14 +32,34 @@ class gui(tk.Tk):
         self.start = tk.Button(self, text = "Start the Game", command=self.getFile) # need to change test to function to call filename
         self.start.pack(side = "bottom", padx=10, pady=5)
 
+    def wordBank(self):
+        # one = "typingTest/lovestory"
+        # two = "typingTest/dontstopbelievin"
+        # three = "typingTest/yesterday"
+        # four = "typingTest/beforehecheats"
+        # five = "typingTest/hundredyears"
+        one = "lovestory"
+        two = "dontstopbelievin"
+        three = "yesterday"
+        four = "beforehecheats"
+        five = "hundredyears"
+
+        choices = [one, two, three, four, five]
+        word = random.choice(choices)
+        return word
+
     def getFile(self):
-        filename = wordBank()
+        filename = self.wordBank()
         # print(filename)
         with open(filename, 'r') as file:
             original = file.read()
         label = tk.Label(self, text=original)
         label.pack()
         self.start.destroy()
+
+    def userInput(self):
+        print("stuff")
+    
 
 def main():
     one = gui()

### 2024-03-24 paper/paper.tex
Update paper.tex

--- 2024-02-27 paper/paper.tex
@@
 \section{Introduction}
-This project will focus on people's ability to type with distractions such as different types of music playing and then will test their cognitive ability to focus on a hand/eye coordination test in which we will test how well they can match shapes by measuring speed and accuracy.
-The purpose of the two-part test is to help test if the music is too much of a distraction or will help the people be more efficient at their work. 
+This project will focus on people's ability to type with distractions such as different types of music playing.
+Then it will test their cognitive ability to focus on a hand/eye coordination test in which we will test how well they can match shapes by measuring speed and accuracy.
+The two-part test aims to help test if the music is too distracting or will help the people be more efficient at their work. 
 This is important because many people do their homework or jobs while listening to music and should they make a mistake, it could end up costing someone their grade or the mistake at work has a cascading effect to cause more errors in their work.
@@
 
-\section{Methodoloy}
-methods
-test\cite{AudioDistractionsAshley}
+\section{Methodology}
+After obtaining consent from all participants, they will proceed to take the typing test.
+The test will present lyrics from popular songs within a graphical user interface (GUI).
+The interface will automatically calculate typing speed and accuracy in the program's backend, allowing participants to focus solely on completing the test.
+Each participant will complete the typing test under three conditions: Music with lyrics, Music without lyrics, and No music (silent condition).
+Multiple levels of music intensity may be utilized within each condition to assess varying degrees of distraction.
+
+Following the typing test, participants will proceed to the cognitive task component of the study, which will also be conducted under the three aforementioned conditions.
+% Further details on the cognitive task will be provided in subsequent sections.
+They will then move on the the QBTest?.
+% This will need to be re-written.
+
+This is a placeholder for a citation cos otherwise the compiler throws errors \cite{AudioDistractionsAshley}.
 

### 2024-03-25 typingTest/class.py
outputs the accuracy and time to user

@@ -38,15 +38,9 @@ class gui(tk.Tk):
         self.endTime = 0
         self.accuracy = 0
 
-
         self.mainloop()
 
     def wordBank(self):
-        # one = "typingTest/lovestory"
-        # two = "typingTest/dontstopbelievin"
-        # three = "typingTest/yesterday"
-        # four = "typingTest/beforehecheats"
-        # five = "typingTest/hundredyears"
         one = "lovestory"
         two = "dontstopbelievin"
         three = "yesterday"
@@ -78,13 +72,18 @@ class gui(tk.Tk):
     def userAccuracy(self):
         temp = self.typingArea.get("1.0", 'end-1c')
         self.inputFromUser = temp.split()
-        self.accuracy = sum(100 for x,y in zip(self.inputWords, self.inputFromUser) if x ==y) / self.totalWords
-        print(f'{self.accuracy:.3} accuracy')
+        self.accuracy = (sum(1 for x,y in zip(self.inputWords, self.inputFromUser) if x ==y) / self.totalWords) * 100
+        if self.accuracy < 100:
+            accuracyLabel = tk.Label(self, text = f'{self.accuracy:.3}% accuracy')
+        else:
+            accuracyLabel = tk.Label(self, text = f'{self.accuracy}% accuracy')
+        accuracyLabel.pack()
 
     def checkResults(self):
         self.endTime = time.time()
         self.done.destroy()
-        print("Attempt took",time.strftime("%H:%M:%S", time.gmtime(self.endTime - self.startTime)))
+        timeLabel = tk.Label(self, text = f'Attempt took {time.strftime("%H:%M:%S", time.gmtime(self.endTime - self.startTime))}')
+        timeLabel.pack()
         self.userAccuracy()
 
 def main():

### 2024-03-25 typingTest/class.py
changed fg and bg text colors

@@ -25,7 +25,7 @@ class gui(tk.Tk):
         # self.typingWindow.place(x=100, y = 100)
         self.typingWindow.pack(side = 'bottom')
 
-        self.typingArea = tk.Text(self.typingWindow, wrap='w', padx=5, pady=5, fg='green', bg='black')
+        self.typingArea = tk.Text(self.typingWindow, wrap='w', padx=5, pady=5, fg='black', bg='white')
         self.typingArea.pack()
 
         self.done = tk.Button(self, text='Done', command=self.checkResults)

### 2024-03-25 typingTest/class.py
fixed the font size

@@ -12,7 +12,7 @@ class gui(tk.Tk):
         self.maxsize(1000, 800)
         self.title("Typing Test")
         self.config(padx=50, pady=10)
-        self.instructions = tk.Label(text = "Type the prompt. The timer start at the first keystroke. To end the timer, use the mouse to hit the text box.") 
+        self.instructions = tk.Label(font=('Arial', 14),text = "Type the prompt. The timer start at the first keystroke. To end the timer, use the mouse to hit the text box.") 
         self.instructions.pack() # add the label to the window
 
         self.file = tk.Button(self, text = "Get the Typing Test", command=self.getFile)
@@ -25,7 +25,7 @@ class gui(tk.Tk):
         # self.typingWindow.place(x=100, y = 100)
         self.typingWindow.pack(side = 'bottom')
 
-        self.typingArea = tk.Text(self.typingWindow, wrap='w', padx=5, pady=5, fg='black', bg='white')
+        self.typingArea = tk.Text(self.typingWindow, wrap='w', padx=5, pady=5, fg='black', bg='white', font='14')
         self.typingArea.pack()
 
         self.done = tk.Button(self, text='Done', command=self.checkResults)
@@ -58,7 +58,7 @@ class gui(tk.Tk):
             self.song = original
             self.inputWords = original.split()
             self.totalWords = len(self.inputWords)
-        label = tk.Label(self, text=original)
+        label = tk.Label(self, text=original, font=('Arial', 14))
         label.pack()
         self.file.destroy()
         self.userInput()
@@ -74,15 +74,16 @@ class gui(tk.Tk):
         self.inputFromUser = temp.split()
         self.accuracy = (sum(1 for x,y in zip(self.inputWords, self.inputFromUser) if x ==y) / self.totalWords) * 100
         if self.accuracy < 100:
-            accuracyLabel = tk.Label(self, text = f'{self.accuracy:.3}% accuracy')
+            accuracyLabel = tk.Label(self, text = f'{self.accuracy:.3}% accuracy', font=('Arial', 20))
         else:
-            accuracyLabel = tk.Label(self, text = f'{self.accuracy}% accuracy')
+            accuracyLabel = tk.Label(self, text = f'{self.accuracy}% accuracy', font=('Arial', 20))
         accuracyLabel.pack()
+        self.typingArea.destroy()
 
     def checkResults(self):
         self.endTime = time.time()
         self.done.destroy()
[…]

### 2024-03-25 typingTest/class.py
update instructions

@@ -7,12 +7,12 @@ class gui(tk.Tk):
     def __init__(self):
         super().__init__()
 
-        self.geometry("800x600") # Horizontal x Vertical
-        self.minsize(800, 600)
-        self.maxsize(1000, 800)
+        self.geometry("800x700+400+200") # Horizontal x Vertical
+        self.minsize(800, 700)
+        self.maxsize(1500, 800)
         self.title("Typing Test")
         self.config(padx=50, pady=10)
-        self.instructions = tk.Label(font=('Arial', 14),text = "Type the prompt. The timer start at the first keystroke. To end the timer, use the mouse to hit the text box.") 
+        self.instructions = tk.Label(wraplength=700, justify='center',font=('Arial', 14), text = "Type the prompt. The timer starts at the first keystroke. To end the typing portion, use the mouse to hit done. The QB test will then start.") 
         self.instructions.pack() # add the label to the window
 
         self.file = tk.Button(self, text = "Get the Typing Test", command=self.getFile)

### 2024-03-25 paper/paper.tex
swap to correct template

@@
-\documentclass[sigconf]{acmart}
+\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
+% documentclass was [sigconf]{acmart} changed to match with the given overleaf link
+
 \AtBeginDocument{%
@@
 
+\setcopyright{acmcopyright}
+\copyrightyear{2024}
+\acmYear{2024}
+\acmDOI{XXXXXXX.XXXXXXX}
+
 \begin{document}
@@
 \author{Jonquill Howlett}
+\email{jonquill.howlett@colostate.edu}
 \affiliation{%
@@
 }
-\email{jonquill.howlett@colostate.edu}
 
 \author{Lianna Hoag}
+\email{jonquill.howlett@colostate.edu} %update email 
 \affiliation{%
@@
 }
-\email{jonquill.howlett@colostate.edu} %update email
 
 \author{Shea Spalding}
+\email{jonquill.howlett@colostate.edu} %update email 
 \affiliation{%
@@
 }
-\email{jonquill.howlett@colostate.edu} %update email
 
-\renewcommand{\shortauthors}{J. Howlett} %I don't know how to format this for three authors
+\renewcommand{\shortauthors}{Howlett, Hoag, Spalding} %I don't know how to format this for three authors 
+% the template does not show any shortauthors
 
 \begin{abstract}
-abstract
+The abstract does not get added until after the project is finished or nearly finished.
 \end{abstract}
@@
 
-This is a placeholder for a citation cos otherwise the compiler throws errors \cite{AudioDistractionsAshley}.
+This is a placeholder for a citation cos otherwise the compiler throws errors~\cite{AudioDistractionsAshley}.
 

### 2024-03-26 paper/paper.tex

@@
 
+\section{Eye Tracking Introduction}
+Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements.
+In this study, we incorporate the EyeWriter 2.0 to track participants' eye movements during the QBTest, a hand-eye coordination task.
+
+The EyeWriter 2.0 offers high-resolution tracking, capturing gaze patterns and fixations with accuracy.
+By analyzing participants' eye movements during the QBTest under different music conditions, we aim to understand how distractions, such as music, influence visual attention and cognitive performance.
+
+Understanding the impact of music on cognitive response time and typing efficiency, as measured by the QBTest and eye tracking, can provide valuable insights for improving work and study environments where music is commonly used as a background stimulus.
+
 \subsection[short]{Participants}

### 2024-03-26 paper/paper.tex
Intro for Typing Test and QBTest

@@
 
+\section{QBTest Introduction}
+The Quantified Behavioral Test (QBTest) is a well-established tool for assessing cognitive function, particularly in measuring hand-eye coordination, speed, and accuracy.
+Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions.
+
+In this study, the QBTest serves as a central component for evaluating participants' cognitive response time and typing efficiency under various music conditions.
+By administering the QBTest alongside eye tracking using EyeWriter 2.0, we aim to understand the impact of music on cognitive function and task performance.
+
+The QBTest's ability to quantify cognitive performance makes it an ideal tool for this study, allowing us to measure the effects of music on participants' ability to focus, process information, and perform tasks accurately.
+Through this research, we seek to provide insights that can enhance our understanding of how environmental factors, such as music, influence cognitive processes.
+
+\section{Typing Test Introduction}
+Typing proficiency is a fundamental skill in today's digital age, essential for academic and professional success.
+However, various factors can influence typing efficiency, including environmental stimuli such as music.
+Understanding how music affects typing speed and accuracy is crucial for optimizing work and study environments.
+
+This study uses a typing test to assess participants' typing performance under different music conditions.
+The test presents participants with lyrics from popular songs, simulating a real-world typing scenario where individuals may listen to music while working or studying.
+
+By measuring typing speed and accuracy under conditions of music with lyrics, music without lyrics, and no music (silent condition), we aim to determine the impact of music on typing efficiency.
+This research will contribute to our understanding of how environmental factors, such as music, can affect cognitive processes related to typing and may have practical implications for improving productivity in various settings.
+
 \subsection[short]{Participants}

### 2024-03-28 paper/paper.tex
moved introductions to intro section and changed to subsections

@@
-\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
+\documentclass[manuscript, screen]{acmart} %removing review removes the numbers on left side
 % documentclass was [sigconf]{acmart} changed to match with the given overleaf link
@@
 
+\subsection{Eye Tracking}
+Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements.
+In this study, we incorporate the EyeWriter 2.0 to track participants' eye movements during the QBTest, a hand-eye coordination task.
+
+The EyeWriter 2.0 offers high-resolution tracking, capturing gaze patterns and fixations with accuracy.
+By analyzing participants' eye movements during the QBTest under different music conditions, we aim to understand how distractions, such as music, influence visual attention and cognitive performance.
+
+Understanding the impact of music on cognitive response time and typing efficiency, as measured by the QBTest and eye tracking, can provide valuable insights for improving work and study environments where music is commonly used as a background stimulus.
+
+\subsection{QBTest}
+The Quantified Behavioral Test (QBTest) is a well-established tool for assessing cognitive function, particularly in measuring hand-eye coordination, speed, and accuracy.
+Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions.
+
+In this study, the QBTest serves as a central component for evaluating participants' cognitive response time and typing efficiency under various music conditions.
+By administering the QBTest alongside eye tracking using EyeWriter 2.0, we aim to understand the impact of music on cognitive function and task performance.
+
+The QBTest's ability to quantify cognitive performance makes it an ideal tool for this study, allowing us to measure the effects of music on participants' ability to focus, process information, and perform tasks accurately.
+Through this research, we seek to provide insights that can enhance our understanding of how environmental factors, such as music, influence cognitive processes.
+
+\subsection{Typing Test}
+Typing proficiency is a fundamental skill in today's digital age, essential for academic and professional success.
+However, various factors can influence typing efficiency, including environmental stimuli such as music.
+Understanding how music affects typing speed and accuracy is crucial for optimizing work and study environments.
+
+This study uses a typing test to assess participants' typing performance under different music conditions.
+The test presents participants with lyrics from popular songs, simulating a real-world typing scenario where individuals may listen to music while working or studying.
+
+By measuring typing speed and accuracy under conditions of music with lyrics, music without lyrics, and no music (silent condition), we aim to determine the impact of music on typing efficiency.
+This research will contribute to our understanding of how environmental factors, such as music, can affect cognitive processes related to typing and may have practical implications for improving productivity in various settings.
+
 \section{Methodology}
@@
 This is a placeholder for a citation cos otherwise the compiler throws errors~\cite{AudioDistractionsAshley}.
-
-\section{Eye Tracking Introduction}
-Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements.
-In this study, we incorporate the EyeWriter 2.0 to track participants' eye movements during the QBTest, a hand-eye coordination task.
-
-The EyeWriter 2.0 offers high-resolution tracking, capturing gaze patterns and fixations with accuracy.
-By analyzing participants' eye movements during the QBTest under different music conditions, we aim to understand how distractions, such as music, influence visual attention and cognitive performance.
-
-Understanding the impact of music on cognitive response time and typing efficiency, as measured by the QBTest and eye tracking, can provide valuable insights for improving work and study environments where music is commonly used as a background stimulus.
-
-\section{QBTest Introduction}
-The Quantified Behavioral Test (QBTest) is a well-established tool for assessing cognitive function, particularly in measuring hand-eye coordination, speed, and accuracy.
-Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions.
-
-In this study, the QBTest serves as a central component for evaluating participants' cognitive response time and typing efficiency under various music conditions.
-By administering the QBTest alongside eye tracking using EyeWriter 2.0, we aim to understand the impact of music on cognitive function and task performance.
-
-The QBTest's ability to quantify cognitive performance makes it an ideal tool for this study, allowing us to measure the effects of music on participants' ability to focus, process information, and perform tasks accurately.
-Through this research, we seek to provide insights that can enhance our understanding of how environmental factors, such as music, influence cognitive processes.
-
-\section{Typing Test Introduction}
-Typing proficiency is a fundamental skill in today's digital age, essential for academic and professional success.
-However, various factors can influence typing efficiency, including environmental stimuli such as music.
-Understanding how music affects typing speed and accuracy is crucial for optimizing work and study environments.
-
-This study uses a typing test to assess participants' typing performance under different music conditions.
-The test presents participants with lyrics from popular songs, simulating a real-world typing scenario where individuals may listen to music while working or studying.
-
-By measuring typing speed and accuracy under conditions of music with lyrics, music without lyrics, and no music (silent condition), we aim to determine the impact of music on typing efficiency.
-This research will contribute to our understanding of how environmental factors, such as music, can affect cognitive processes related to typing and may have practical implications for improving productivity in various settings.
 

### 2024-03-29 paper/paper.tex
update authors

@@
 
-\author{Lianna Hoag}
-\email{jonquill.howlett@colostate.edu} %update email 
+\author{Shea Spalding}
+\email{Shea.Spalding@colostate.edu} %update email 
 \affiliation{%
@@
 
-\author{Shea Spalding}
-\email{jonquill.howlett@colostate.edu} %update email 
-\affiliation{%
-  \institution{Colorado State University}
-  \city{Fort Collins}
-  \state{Colorado}
-  \country{USA}
-  \postcode{80525-0650} %chktex 8 %the rest of the zip will need to be corrected
-}
-
-\renewcommand{\shortauthors}{Howlett, Hoag, Spalding} %I don't know how to format this for three authors 
+\renewcommand{\shortauthors}{Howlett, Spalding} %I don't know how to format this for three authors 
 % the template does not show any shortauthors
@@
 
+% Put the related works here
+% \section{Related Works}
+
 \section{Methodology}
@@
 Apparatus
+\subsubsection{EyeWriter 2.0}
+\subsubsection{QB Test}
+\subsubsection{Typing Test}
+
+I will add typing methodology here.
 

### 2024-03-29 paper/paper.tex
changed part of methodology to past tense

@@
-\documentclass[manuscript, screen]{acmart} %removing review removes the numbers on left side
+\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
 % documentclass was [sigconf]{acmart} changed to match with the given overleaf link
@@
 
-\renewcommand{\shortauthors}{Howlett, Spalding} %I don't know how to format this for three authors 
+\renewcommand{\shortauthors}{Howlett, Spalding}
 % the template does not show any shortauthors
@@
 In this study, we incorporate the EyeWriter 2.0 to track participants' eye movements during the QBTest, a hand-eye coordination task.
-
 The EyeWriter 2.0 offers high-resolution tracking, capturing gaze patterns and fixations with accuracy.
 By analyzing participants' eye movements during the QBTest under different music conditions, we aim to understand how distractions, such as music, influence visual attention and cognitive performance.
-
 Understanding the impact of music on cognitive response time and typing efficiency, as measured by the QBTest and eye tracking, can provide valuable insights for improving work and study environments where music is commonly used as a background stimulus.
@@
 Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions.
-
+% This would be a good place to put a citation.
 In this study, the QBTest serves as a central component for evaluating participants' cognitive response time and typing efficiency under various music conditions.
 By administering the QBTest alongside eye tracking using EyeWriter 2.0, we aim to understand the impact of music on cognitive function and task performance.
-
 The QBTest's ability to quantify cognitive performance makes it an ideal tool for this study, allowing us to measure the effects of music on participants' ability to focus, process information, and perform tasks accurately.
@@
 Understanding how music affects typing speed and accuracy is crucial for optimizing work and study environments.
-
 This study uses a typing test to assess participants' typing performance under different music conditions.
 The test presents participants with lyrics from popular songs, simulating a real-world typing scenario where individuals may listen to music while working or studying.
-
 By measuring typing speed and accuracy under conditions of music with lyrics, music without lyrics, and no music (silent condition), we aim to determine the impact of music on typing efficiency.
@@
 \section{Methodology}
-After obtaining consent from all participants, they will proceed to take the typing test.
-The test will present lyrics from popular songs within a graphical user interface (GUI).
-The interface will automatically calculate typing speed and accuracy in the program's backend, allowing participants to focus solely on completing the test.
+% After obtaining consent from all participants, they will proceed to take the typing test. The test will present lyrics from popular songs within a graphical user interface (GUI). 
+After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
+% The interface will automatically calculate typing speed and accuracy in the program's backend, allowing participants to focus solely on completing the test.
 Each participant will complete the typing test under three conditions: Music with lyrics, Music without lyrics, and No music (silent condition).
-Multiple levels of music intensity may be utilized within each condition to assess varying degrees of distraction.
+The interface automatically calculated typing speed and accuracy in the program's backend, allowing participants to focus soley on completing the test.
+Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
+% Multiple levels of music intensity may be utilized within each condition to assess varying degrees of distraction.
+Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.
 
-Following the typing test, participants will proceed to the cognitive task component of the study, which will also be conducted under the three aforementioned conditions.
-% Further details on the cognitive task will be provided in subsequent sections.
-They will then move on the the QBTest?.
-% This will need to be re-written.
+% Following the typing test, participants will proceed to the cognitive task component of the study, which will also be conducted under the three aforementioned conditions.
+Following the typing test, participants proceeded to to the cognitive task component of the study, which were also conducted under the three aforementioned conditions.
+While the participants did the cognitive task of a quantified behavioral test, they wore the EyeWriter 2.0 glasses that we specially built for this study.
+% Further details on the cognitive task will be provided in subsequent sections. They will then move on the the QBTest?. % This will need to be re-written.
 
@@
 \subsection[short]{Apparatus}
-Apparatus
+
 \subsubsection{EyeWriter 2.0}
@@
 \subsubsection{Typing Test}
-
-I will add typing methodology here.
+The typing program was written in Python and compiled using Python3.9.
+While python can run on any device that has python installed, this study only used Macbook Pros running on Sonoma or MacOS 14.
+The singularity of the devices was used as the center of the screen for the typing test was hard coded when setting the starting position of the window for the typing test.
 

### 2024-03-29 paper/paper.tex
add pictures and portion of methodology

@@
 \documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
-% documentclass was [sigconf]{acmart} changed to match with the given overleaf link
+% \documentclass was [sigconf]{acmart} changed to match with the given overleaf link
+% \documentclass[sigconf]{acmart}
 
@@
 \usepackage{graphicx} %% For pictures
+\graphicspath{{./pics/}}
 \usepackage[section]{placeins} %% used to keep the images in the section that I want them in
@@
 This project will focus on people's ability to type with distractions such as different types of music playing.
-Then it will test their cognitive ability to focus on a hand/eye coordination test in which we will test how well they can match shapes by measuring speed and accuracy.
+It will then test their cognitive ability to focus on a hand/eye coordination test in which we will test how well they can match shapes by measuring speed and accuracy.
 The two-part test aims to help test if the music is too distracting or will help the people be more efficient at their work. 
@@
 \section{Methodology}
-% After obtaining consent from all participants, they will proceed to take the typing test. The test will present lyrics from popular songs within a graphical user interface (GUI). 
 After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
-% The interface will automatically calculate typing speed and accuracy in the program's backend, allowing participants to focus solely on completing the test.
-Each participant will complete the typing test under three conditions: Music with lyrics, Music without lyrics, and No music (silent condition).
 The interface automatically calculated typing speed and accuracy in the program's backend, allowing participants to focus soley on completing the test.
 Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
-% Multiple levels of music intensity may be utilized within each condition to assess varying degrees of distraction.
 Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.
+The GUI of the typing test was built with simplicity in mind.
+The starting window was pulled up so as not to confuse participants with the code as seen in Figure 1.
+The participants saw Figure 2 while the test is running, while Figure 3 is the signifier that the typing portion is finished.
 
-% Following the typing test, participants will proceed to the cognitive task component of the study, which will also be conducted under the three aforementioned conditions.
+\begin{figure}
+  \includegraphics[width=0.3\textwidth]{typing_test_1}
+  \caption{Starting window of typing test}
+  \Description{Image of the starting windows of the typing test}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=0.3\textwidth]{typing_test_2}
+  \caption{Test started}
+  \Description{Image of the test with the lyrics that the user will type}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=0.3\textwidth]{typing_test_3}
+  \caption{Test finished}
+  \Description{Image of the finished test}
+\end{figure}
+
+They were given the instructions in the GUI with the text area where their text goes clearly visible and the only button in the window to start the test and timer.
+After they hit the ``Get the Typing Test'' button, the lyrics of the randomly selected songs were displayed for the user to type.
+The text box for the users was already in focus with a ``Done'' button.
+After the users hit ``Done'', their accuracy and speed were presented.
+
 Following the typing test, participants proceeded to to the cognitive task component of the study, which were also conducted under the three aforementioned conditions.
@@
 \subsection[short]{Participants}
-Participants
+Approximately twenty participants were recruited from Colorado State University. Ten males and ten females all in the age range of 18-99. There were no %chktex 8
+restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
+They have all previously either learned to type at primary school or through necessity.
 
-\subsection[short]{Apparatus}
+\subsection[short]{Apparatus}  % Do we want to change this to Equipment? 
+% This may not need to be broken into subsections. Will decide before we resubmit. 
+Participants used two different Macbook Pros in this study. One Macbook ran the typing test while the other was used for the QBTest. 
+The keyboard on the second Macbook was inaccessible as the eye tracker positioning would block the majority of the keys should they have 
+taken the typing test and QBTest on a singular device.
 

### 2024-03-29 paper/paper.tex
indent in vscode to fold

@@
-\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
+% \documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
 % \documentclass was [sigconf]{acmart} changed to match with the given overleaf link
-% \documentclass[sigconf]{acmart}
+\documentclass[sigconf]{acmart}
 
@@
 % Put the related works here
-% \section{Related Works}
+\section{Related Works}
+While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
+studies that attempt to determine the answer.
 

### 2024-03-30 paper/paper.tex
start related works

--- 2024-03-29 paper/paper.tex
@@
 % Put the related works here
-% \section{Related Works}
+\section{Related Works}
+While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
+studies that attempt to determine the answer. The other studies attempted to search for this answer by
+focusing on word processing on a computer with the background music and the user's ability to formulate sentences~\cite{ransdell2001141}, 
+or determining if background music help users to keep their attention on their task at hand~\cite{kiss2021effect}.
 
@@
 
-This is a placeholder for a citation cos otherwise the compiler throws errors~\cite{AudioDistractionsAshley}.
-
   \subsection[short]{Participants}

### 2024-03-30 paper/paper.tex
add related works about music and cognitive function

@@
   \country{USA}
-  \postcode{80525-0650} %chktex 8 %the rest of the zip will need to be corrected
+  \postcode{80523-1873} %chktex 8
 }
@@
 
-% Put the related works here
 \section{Related Works}
@@
 or determining if background music help users to keep their attention on their task at hand~\cite{kiss2021effect}.
+Similar to~\cite{kiss2021effect},~\cite{mathew2022inherently} also examined how motivation and music were used hand-in-hand on ``a time-consuming task and task performance''.
+A different study done in 2010 again found similar results of music both being a hinderance and benefit~\cite{AudioDistractionsAshley}.
+According to~\cite{Gonzalez_Aiello_2019}, the degree of cognitive function may be based on an individual's personality.
+
+Although~\cite{ransdell2001141} suggests that the music is a detriment, those with ``musical training and high working memory span wrote better essays with longer sentences'.
+This suggests that while the music slowed down the participants, it did not necessarily lower their cognitive ability in typing on their computer while focusing on forming text for the written essay for this particular study.
+For~\cite{AudioDistractionsAshley}, the music caused enough of a difference in the time that was taken for writing a paragraph but ``there were no signigicant differences in typing speed between the audio distractions''.
+This again may suggest that the participants cognitive ability was not hindered when typing and may transfer to directly after should the participants taken a test measuring their cognitive function.
+The slow timing was again seen in~\cite{Gonzalez_Aiello_2019} in which ``music generally impaired performance on a complex task but improved performance on a simple task''.
+
+The study done through~\cite{kiss2021effect} saw opposite results as to~\cite{Gonzalez_Aiello_2019}.
+The music or background noise ``enchanced'' the reaction time and performance of the tasks that we given to be completed.
+The results from~\cite{mathew2022inherently} were split.
+The music was a detriment for logic puzzles in the user's accuracy but aided in the efficiency of a writing task.
 

### 2024-03-31 eyeTracker/src/Tracking/brightDarkFinder.h
Add files via upload

@@ -1,0 +1,18 @@
+#pragma once
+
+#include "ofMain.h"
+#include "ofxOpenCv.h"
+#include "ofxCvGrayscaleAdvanced.h"
+
+class brightDarkFinder {
+	
+	public:
+		
+		bool getBrightEyeDarkEye(ofxCvGrayscaleAdvanced & img, ofRectangle & roi);
+		void drawAutoThresholdBrightnessGraph(int x, int y, bool bError);
+	
+		vector	<float>		averageVec;
+		float				pixelAvg;
+		float				pixelAvginTenframes;
+
+};

### 2024-03-31 eyeTracker/src/Tracking/eyeTracker.cpp

@@ -1,0 +1,204 @@
+#include "eyeTracker.h"
+//--------------------------------------------------------------
+eyeTracker::eyeTracker() {
+	
+	bFoundOne	= false;
+}
+
+//----------------------------------------------------
+void eyeTracker::setup(int width, int height) {
+	
+	w = width;					// IM.width
+	h = height;					// IM.height
+	magRatio = 4;				// for accurate detection. width x magRatio, height x magRatio
+	divisor = 2;				// for eyeFinder, make the picture smaller to reduce computation
+	
+	// TODO: now it can't work with divisor = 1, let's debug this problem.
+	
+	printf("VideoWidth, VideoHeight = %d, %d \n", w, h);
+	
+	currentImg.allocate(w, h);
+	currentEyePoint	= ofPoint(0, 0);
+	
+	targetRect.x = 0;
+	targetRect.y = 0;
+	targetRect.width = 128;		// for zach 128, 88 was default, might ought to be devided by 4 or 2(for resize)?
+	targetRect.height = 64;
+	
+	magCurrentImg.allocate(targetRect.width * magRatio, targetRect.height * magRatio);
+	smallCurrentImg.allocate(w/divisor, h/divisor);
+	
+	brightEyeImg.allocate(targetRect.width, targetRect.height);
+	darkEyeImg.allocate(targetRect.width, targetRect.height);
+		
+	eFinder.setup(w, h, targetRect.width, targetRect.height, divisor);
+	pFinder.setup(targetRect.width, targetRect.height, magRatio, w, h);
+	gFinder.setup(targetRect.width, targetRect.height, magRatio, w, h);
+	
+	thresCal.setup(targetRect.width, targetRect.height, divisor);
+	homographyCal.setup(100, 50, targetRect.width * magRatio, targetRect.height * magRatio);
+	
+	bUseGlintinBrightEye = false;	
+	bFoundEye = false;
+	
+	// initialize status.
+	tState.bEyeFound = false;
+	tState.bGoodAlternation = false;
+	tState.bGlintInBrightEyeFound = false;
+	tState.bGlintInDarkEyeFound = false;
+	tState.bPupilFound = false;
+	
+}
+
+//----------------------------------------------------
+void eyeTracker::update(ofxCvGrayscaleImage & grayImgFromCam) {
+	
+	// initialize status, keep status for pupil & glint.
+	tState.bEyeFound = false;
[…]

### 2024-03-31 paper/paper.tex

@@
 \author{Shea Spalding}
-\email{Shea.Spalding@colostate.edu} %update email 
+\email{Shea1@colostate.edu} %update email 
 \affiliation{%
@@
   \country{USA}
-  \postcode{80523-1873} %chktex 8
+  \postcode{80521-1873} %chktex 8
 }
@@
 focusing on word processing on a computer with the background music and the user's ability to formulate sentences~\cite{ransdell2001141}, 
-or determining if background music help users to keep their attention on their task at hand~\cite{kiss2021effect}.
+or determining if background music helps users to keep their attention on their task at hand~\cite{kiss2021effect}.
 Similar to~\cite{kiss2021effect},~\cite{mathew2022inherently} also examined how motivation and music were used hand-in-hand on ``a time-consuming task and task performance''.
-A different study done in 2010 again found similar results of music both being a hinderance and benefit~\cite{AudioDistractionsAshley}.
+A different study done in 2010 again found similar results of music both being a hindrance and benefit~\cite{AudioDistractionsAshley}.
 According to~\cite{Gonzalez_Aiello_2019}, the degree of cognitive function may be based on an individual's personality.
@@
 This suggests that while the music slowed down the participants, it did not necessarily lower their cognitive ability in typing on their computer while focusing on forming text for the written essay for this particular study.
-For~\cite{AudioDistractionsAshley}, the music caused enough of a difference in the time that was taken for writing a paragraph but ``there were no signigicant differences in typing speed between the audio distractions''.
-This again may suggest that the participants cognitive ability was not hindered when typing and may transfer to directly after should the participants taken a test measuring their cognitive function.
+For~\cite{AudioDistractionsAshley}, the music caused enough of a difference in the time that was taken for writing a paragraph but ``there were no significant differences in typing speed between the audio distractions''.
+This again may suggest that the participant's cognitive ability was not hindered when typing and may transfer directly after should the participants have taken a test measuring their cognitive function.
 The slow timing was again seen in~\cite{Gonzalez_Aiello_2019} in which ``music generally impaired performance on a complex task but improved performance on a simple task''.
@@
 The study done through~\cite{kiss2021effect} saw opposite results as to~\cite{Gonzalez_Aiello_2019}.
-The music or background noise ``enchanced'' the reaction time and performance of the tasks that we given to be completed.
+The music or background noise ``enhanced'' the reaction time and performance of the tasks that are given to be completed.
 The results from~\cite{mathew2022inherently} were split.
@@
 After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
-  The interface automatically calculated typing speed and accuracy in the program's backend, allowing participants to focus soley on completing the test.
+The interface automatically calculated typing speed and accuracy in the program's backend, allowing participants to focus solely on completing the test.
 Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
@@
 
-  They were given the instructions in the GUI with the text area where their text goes clearly visible and the only button in the window to start the test and timer.
+They were given the instructions in the GUI with the text area where their text is clearly visible and the only button in the window to start the test and timer.
 After they hit the ``Get the Typing Test'' button, the lyrics of the randomly selected songs were displayed for the user to type.
@@
 
-  Following the typing test, participants proceeded to to the cognitive task component of the study, which were also conducted under the three aforementioned conditions.
-While the participants did the cognitive task of a quantified behavioral test, they wore the EyeWriter 2.0 glasses that we specially built for this study.
+Following the typing test, participants proceeded to the cognitive task component of the study, which was also conducted under the three aforementioned conditions.
+While the participants did the cognitive task of a quantified behavioral test, their eye movement will be tracked by the EyeWriter 2.0 camera that we specially built for this study.
+The EyeWriter system consists of a camera mounted on the participant's laptop, which tracks eye movements and allows for precise measurement of gaze direction and fixation duration.
+
+Participants were seated in a comfortable position facing the laptop screen.
+They were instructed to follow a series of calibration points displayed on the screen to calibrate the eye-tracking system.
+This calibration process ensured accurate measurement of eye movements during the subsequent tasks.
+
+During the cognitive task component of the study, participants performed a quantified behavioral test (QBTest) while their eye movements were tracked by the EyeWriter 2.0 camera mounted on the laptop.
+The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
 % Further details on the cognitive task will be provided in subsequent sections. They will then move on the the QBTest?. % This will need to be re-written.

### 2024-03-31 paper/paper.tex
Update paper.tex

@@
 % This may not need to be broken into subsections. Will decide before we resubmit. 
-Participants used two different Macbook Pros in this study. One Macbook ran the typing test while the other was used for the QBTest. 
-The keyboard on the second Macbook was inaccessible as the eye tracker positioning would block the majority of the keys should they have 
-taken the typing test and QBTest on a singular device.
+Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup.
+One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it.
+The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test.
+
+QBTest MacBook Pro with Eye Tracker: This MacBook Pro was dedicated to conducting the QBTest.
+It had the eye tracker mounted on it, which made it difficult to access the keyboard for typing.
+Participants used this MacBook Pro for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test.
+
+Typing Test MacBook Pro: The second MacBook Pro was used for the typing test.
+Since it did not have the eye tracker mounted on it, participants could easily access the keyboard and perform the typing test without any interference from the eye tracker.
+
+Using two separate MacBook Pros allowed for the independent administration of the QBTest and typing test, ensuring that participants could perform each task without any physical hindrance from the eye tracker.
 

### 2024-03-31 paper/paper.tex
add eyewriter

@@
 % This may not need to be broken into subsections. Will decide before we resubmit. 
-Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup.
+Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 1.
 One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it.
@@
 Since it did not have the eye tracker mounted on it, participants could easily access the keyboard and perform the typing test without any interference from the eye tracker.
-
 Using two separate MacBook Pros allowed for the independent administration of the QBTest and typing test, ensuring that participants could perform each task without any physical hindrance from the eye tracker.
@@
 \subsubsection{EyeWriter 2.0}
-\subsubsection{QB Test}
+The IR camera captures the eye movements of the participant.
+It is mounted on the laptop that participants use for the QBTest, allowing for the tracking of eye movements during the test.
+IR LEDs are used to illuminate the eye to enhance the visibility of the eye for tracking purposes. 
+These LEDs are also mounted on the laptop along with the IR camera. 
+The mounting system holds the IR camera and IR LEDs in place relative to the participant's eye. 
+It ensures that the camera has a clear view of the eye for accurate tracking. 
+Cables are used to connect the IR camera and IR LEDs to the laptop. These cables transmit data and power between the components.
+% \subsubsection{QB Test} 
 \subsubsection{Typing Test}
 The typing program was written in Python and compiled using Python3.9.
-While python can run on any device that has python installed, this study only used Macbook Pros running on Sonoma or MacOS 14.
+While python can run on any device that has python installed, this study only used the two Macbook Pros.
 The singularity of the devices was used as the center of the screen for the typing test was hard coded when setting the starting position of the window for the typing test.

### 2024-04-09 qbTest/qb_test.py
added qb_test.py first try

@@ -1,0 +1,70 @@
+import pygame # type: ignore
+import random
+
+# Initialize pygame
+pygame.init()
+
+# Constants
+WIDTH, HEIGHT = 800, 600
+FPS = 60
+WHITE = (255, 255, 255)
+BLACK = (0, 0, 0)
+RED = (255, 0, 0)
+GREEN = (0, 255, 0)
+BLUE = (0, 0, 255)
+SHAPE_COLORS = [RED, GREEN, BLUE]
+SHAPE_RADIUS = 50
+FLASH_TIME = 1.0  # Time in seconds for each shape to flash
+
+# Function to display text on the screen
+def display_text(screen, text, font, color, position):
+    text_surface = font.render(text, True, color)
+    text_rect = text_surface.get_rect(center=position)
+    screen.blit(text_surface, text_rect)
+
+# Main function to run the QB test
+def run_qb_test():
+    screen = pygame.display.set_mode((WIDTH, HEIGHT))
+    pygame.display.set_caption("QB Test - Press Space for Correct Color")
+
+    clock = pygame.time.Clock()
+    font = pygame.font.Font(None, 36)
+    running = True
+    current_color = random.choice(SHAPE_COLORS)
+    start_time = pygame.time.get_ticks()
+    correct_shape_displayed = False
+
+    while running:
+        screen.fill(WHITE)
+        current_time = (pygame.time.get_ticks() - start_time) / 1000.0
+
+        # Display flashing shape
+        if current_time % (2 * FLASH_TIME) < FLASH_TIME:
+            pygame.draw.circle(screen, current_color, (WIDTH // 2, HEIGHT // 2), SHAPE_RADIUS)
+
+        # Check for user input
+        for event in pygame.event.get():
+            if event.type == pygame.QUIT:
+                running = False
+            elif event.type == pygame.KEYDOWN:
+                if event.key == pygame.K_SPACE:
+                    if current_color == RED:
+                        correct_shape_displayed = True
+                    else:
+                        correct_shape_displayed = False
+
+        # Display instructions and feedback
+        display_text(screen, "Press Space when you see RED", font, BLACK, (WIDTH // 2, HEIGHT - 50))
+
+        if correct_shape_displayed:
+            display_text(screen, "Correct!", font, GREEN, (WIDTH // 2, HEIGHT // 2 + SHAPE_RADIUS + 50))
+        else:
[…]

### 2024-04-09 qbTest/qb_test.py
added README file

@@ -1,5 +1,13 @@
 import pygame # type: ignore
 import random
+import sys
+
+print("Python Interpreter:", sys.executable)
+print("Python Version:", sys.version)
+print("Module Search Paths:")
+
+for path in sys.path:
+    print(path)
 
 # Initialize pygame
 pygame.init()

### 2024-04-09 qbTest/qb_test.py
changes

@@ -1,4 +1,4 @@
-import pygame # type: ignore
+import pygame
 import random
 import sys
 

### 2024-04-10 paper/paper.tex
add subsection Qbtest

@@
 
+\subsubsection{Quantified Behavioral Test}
+The Quantified Behavioral Test or QBTest program was written in Python and compiled using Python3.9.
+The package pygame was used for this interface compared to the package tkinter used for the typing test.
+
 \subsection[short]{Procedure}
@@
 \section{Results and Discussion}
-Results and Discussion
+Within-subjects testing was used.
 

### 2024-04-11 qbTest/qb_test.py
changes to qb

@@ -1,6 +1,7 @@
-import pygame # type: ignore
+import pygame 
 import random
 import sys
+import time  # Import the time module for timing
 
 # Initialize pygame
 pygame.init()
@@ -9,12 +10,12 @@ pygame.init()
 WIDTH, HEIGHT = 800, 600
 FPS = 60
 WHITE = (255, 255, 255)
-BLACK = (0, 0, 0)
 RED = (255, 0, 0)
 GREEN = (0, 255, 0)
 BLUE = (0, 0, 255)
 SHAPE_RADIUS = 50
 FLASH_TIME = 1.0  # Time in seconds for each shape to flash
+PAUSE_TIME = 0.5  # Time in seconds to pause between flashes
 
 # Function to display text on the screen
 def display_text(screen, text, font, color, position):
@@ -30,20 +31,33 @@ def run_qb_test():
     clock = pygame.time.Clock()
     font = pygame.font.Font(None, 36)
     running = True
+    last_flash_time = time.time()  # Track the last time a shape was flashed
+    flash_complete = True  # Flag to track if a flash cycle is complete
 
     while running:
         screen.fill(WHITE)
 
-        # Generate a random color for the shape
-        current_color = random.choice([RED, GREEN, BLUE])
+        current_time = time.time()
 
-        # Display flashing shape (circle)
-        current_time = pygame.time.get_ticks() / 1000.0  # Convert to seconds
-        if current_time % (2 * FLASH_TIME) < FLASH_TIME:
+        if flash_complete:
+            # Generate a random color for the shape
+            current_color = random.choice([RED, GREEN, BLUE])
+            flash_complete = False
+            last_flash_time = current_time  # Reset the last flash time
+
+        # Determine if it's time to show the shape or pause
+        if current_time - last_flash_time < FLASH_TIME:
+            # Display flashing shape (circle)
             pygame.draw.circle(screen, current_color, (WIDTH // 2, HEIGHT // 2), SHAPE_RADIUS)
+        elif current_time - last_flash_time < FLASH_TIME + PAUSE_TIME:
+            # Pause between flashes
+            pass
+        else:
+            # Reset for the next flash cycle
+            flash_complete = True
 
         # Display instructions and feedback text
-        display_text(screen, "Press Space when you see RED", font, BLACK, (WIDTH // 2, HEIGHT - 50))
+        display_text(screen, "Press Space when you see RED", font, (0, 0, 0), (WIDTH // 2, HEIGHT - 50))
 
         # Event handling
         for event in pygame.event.get():

### 2024-04-11 qbTest/qb_test.py
more changes

@@ -16,12 +16,14 @@ BLUE = (0, 0, 255)
 SHAPE_RADIUS = 50
 FLASH_TIME = 1.0  # Time in seconds for each shape to flash
 PAUSE_TIME = 0.5  # Time in seconds to pause between flashes
+FEEDBACK_DISPLAY_TIME = 2.0  # Time in seconds to display feedback (Correct or Wrong)
 
 # Function to display text on the screen
 def display_text(screen, text, font, color, position):
     text_surface = font.render(text, True, color)
     text_rect = text_surface.get_rect(center=position)
     screen.blit(text_surface, text_rect)
+    return text_surface.get_rect()
 
 # Main function to run the QB test
 def run_qb_test():
@@ -32,7 +34,9 @@ def run_qb_test():
     font = pygame.font.Font(None, 36)
     running = True
     last_flash_time = time.time()  # Track the last time a shape was flashed
+    last_feedback_time = 0.0  # Track the last time feedback was displayed
     flash_complete = True  # Flag to track if a flash cycle is complete
+    feedback_displayed = False  # Flag to track if feedback is currently displayed
 
     while running:
         screen.fill(WHITE)
@@ -56,19 +60,31 @@ def run_qb_test():
             # Reset for the next flash cycle
             flash_complete = True
 
-        # Display instructions and feedback text
+        # Display instructions
         display_text(screen, "Press Space when you see RED", font, (0, 0, 0), (WIDTH // 2, HEIGHT - 50))
+
+        # Check for feedback display
+        if current_time - last_feedback_time < FEEDBACK_DISPLAY_TIME and feedback_displayed:
+            # Display the feedback message (Correct or Wrong)
+            display_text(screen, feedback_message, font, feedback_color, feedback_position)
+        else:
+            feedback_displayed = False
 
         # Event handling
         for event in pygame.event.get():
             if event.type == pygame.QUIT:
                 running = False
             elif event.type == pygame.KEYDOWN:
-                if event.key == pygame.K_SPACE:
+                if event.key == pygame.K_SPACE and not feedback_displayed:
                     if current_color == RED:
-                        display_text(screen, "Correct!", font, GREEN, (WIDTH // 2, HEIGHT // 2 + SHAPE_RADIUS + 50))
+                        feedback_message = "Correct!"
+                        feedback_color = GREEN
                     else:
[…]

### 2024-04-16 qbTest/qb_test.py
qbTest score tracker

@@ -17,6 +17,7 @@ SHAPE_RADIUS = 50
 FLASH_TIME = 1.0  # Time in seconds for each shape to flash
 PAUSE_TIME = 0.5  # Time in seconds to pause between flashes
 FEEDBACK_DISPLAY_TIME = 0.65  # Time in seconds to display feedback (Correct or Wrong)
+SCORE_FILE = "scores.txt"  # File to save scores
 
 # Function to display text on the screen
 def display_text(screen, text, font, color, position):
@@ -24,6 +25,12 @@ def display_text(screen, text, font, color, position):
     text_rect = text_surface.get_rect(center=position)
     screen.blit(text_surface, text_rect)
     return text_surface.get_rect()
+
+# Function to save score to a file
+def save_score(score):
+    with open(SCORE_FILE, "a") as file:
+        file.write(f"{score}\n")
+
 
 # Main function to run the QB test
 def run_qb_test():
@@ -37,7 +44,7 @@ def run_qb_test():
     last_feedback_time = 0.0  # Track the last time feedback was displayed
     flash_complete = True  # Flag to track if a flash cycle is complete
     feedback_displayed = False  # Flag to track if feedback is currently displayed
-
+    score = 0
     while running:
         screen.fill(WHITE)
 
@@ -63,6 +70,8 @@ def run_qb_test():
         # Display instructions
         display_text(screen, "Press Space when you see RED", font, (0, 0, 0), (WIDTH // 2, HEIGHT - 50))
 
+
+
         # Check for feedback display
         if current_time - last_feedback_time < FEEDBACK_DISPLAY_TIME and feedback_displayed:
             # Display the feedback message (Correct or Wrong)
@@ -85,6 +94,14 @@ def run_qb_test():
                     feedback_position = (WIDTH // 2, HEIGHT // 2 + SHAPE_RADIUS + 50)
                     last_feedback_time = current_time
                     feedback_displayed = True
+
+        # Check for game end condition (e.g., after 10 rounds)
+        if score >= 10:
+            save_score(score)
+            display_text(screen, f"Game Over! Final Score: {score}", font, (0, 0, 0), (WIDTH // 2, HEIGHT // 2))
+            pygame.display.flip()
+            pygame.time.wait(2000)  # Display final score for 2 seconds
+            running = False
 
         pygame.display.flip()  # Update display
         clock.tick(FPS)  # Cap the frame rate

### 2024-04-16 qbTest/qb_test.py
updates score

@@ -88,6 +88,7 @@ def run_qb_test():
                     if current_color == RED:
                         feedback_message = "Correct!"
                         feedback_color = GREEN
+                        score += 1
                     else:
                         feedback_message = "Wrong!"
                         feedback_color = RED

### 2024-04-17 qbTest/qb_test.py
QBTest with timing

@@ -36,7 +36,7 @@ def save_score(score):
 def run_qb_test():
     screen = pygame.display.set_mode((WIDTH, HEIGHT))
     pygame.display.set_caption("QB Test - Press Space for Red")
-
+    
     clock = pygame.time.Clock()
     font = pygame.font.Font(None, 36)
     running = True
@@ -45,6 +45,8 @@ def run_qb_test():
     flash_complete = True  # Flag to track if a flash cycle is complete
     feedback_displayed = False  # Flag to track if feedback is currently displayed
     score = 0
+    start_time = time.time()
+    
     while running:
         screen.fill(WHITE)
 
@@ -86,18 +88,20 @@ def run_qb_test():
             elif event.type == pygame.KEYDOWN:
                 if event.key == pygame.K_SPACE and not feedback_displayed:
                     if current_color == RED:
-                        feedback_message = "Correct!"
+                        #feedback_message = "Correct!"
                         feedback_color = GREEN
                         score += 1
                     else:
-                        feedback_message = "Wrong!"
+                        #feedback_message = "Wrong!"
                         feedback_color = RED
                     feedback_position = (WIDTH // 2, HEIGHT // 2 + SHAPE_RADIUS + 50)
                     last_feedback_time = current_time
                     feedback_displayed = True
 
-        # Check for game end condition (e.g., after 10 rounds)
-        if score >= 10:
+        # Check for game end condition (e.g., after 2 mins)
+        current_time = time.time()
+        elapsed_time = current_time - start_time
+        if elapsed_time >= 120:  # 120 seconds = 2 minutes
             save_score(score)
             display_text(screen, f"Game Over! Final Score: {score}", font, (0, 0, 0), (WIDTH // 2, HEIGHT // 2))
             pygame.display.flip()

### 2024-04-17 qbTest/qb_test.py
qb error fixes

@@ -88,11 +88,11 @@ def run_qb_test():
             elif event.type == pygame.KEYDOWN:
                 if event.key == pygame.K_SPACE and not feedback_displayed:
                     if current_color == RED:
-                        #feedback_message = "Correct!"
+                        feedback_message = "Correct!"
                         feedback_color = GREEN
                         score += 1
                     else:
-                        #feedback_message = "Wrong!"
+                        feedback_message = "Wrong!"
                         feedback_color = RED
                     feedback_position = (WIDTH // 2, HEIGHT // 2 + SHAPE_RADIUS + 50)
                     last_feedback_time = current_time
@@ -103,7 +103,7 @@ def run_qb_test():
         elapsed_time = current_time - start_time
         if elapsed_time >= 120:  # 120 seconds = 2 minutes
             save_score(score)
-            display_text(screen, f"Game Over! Final Score: {score}", font, (0, 0, 0), (WIDTH // 2, HEIGHT // 2))
+            display_text(screen, f"Correct: {score}", font, (0, 0, 0), (WIDTH // 2, HEIGHT // 2))
             pygame.display.flip()
             pygame.time.wait(2000)  # Display final score for 2 seconds
             running = False

### 2024-04-17 qbTest/qb_test.py
QBTest Start Screen

@@ -39,11 +39,37 @@ def run_qb_test():
     
     clock = pygame.time.Clock()
     font = pygame.font.Font(None, 36)
-    running = True
+    running = False
+    start_screen = True
     last_flash_time = time.time()  # Track the last time a shape was flashed
     last_feedback_time = 0.0  # Track the last time feedback was displayed
     flash_complete = True  # Flag to track if a flash cycle is complete
     feedback_displayed = False  # Flag to track if feedback is currently displayed
+    score = 0
+    start_time = time.time()
+    
+    while start_screen:
+        screen.fill(WHITE)
+        display_text(screen, "QB Test", font, (0, 0, 0), (WIDTH // 2, HEIGHT // 4))
+        display_text(screen, "Press Space to Start", font, (0, 0, 0), (WIDTH // 2, HEIGHT // 2))
+
+        for event in pygame.event.get():
+            if event.type == pygame.QUIT:
+                start_screen = False
+                running = False
+            elif event.type == pygame.KEYDOWN:
+                if event.key == pygame.K_SPACE:
+                    start_screen = False
+                    running = True
+                    break
+
+        pygame.display.flip()
+        clock.tick(FPS)
+
+    last_flash_time = time.time()
+    last_feedback_time = 0.0
+    flash_complete = True
+    feedback_displayed = False
     score = 0
     start_time = time.time()
     

### 2024-04-17 paper/paper.tex
start procedure

@@
 
-\subsection[short]{Apparatus}  % Do we want to change this to Equipment? 
+\subsection[short]{Equipment}  % Do we want to change this to Equipment? 
 % This may not need to be broken into subsections. Will decide before we resubmit. 
-Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 1.
+Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 14.
 One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it.
@@
 \subsection[short]{Procedure}
-Procedure
+After signing consent forms, each participant was explained the overall concept of what they would be doing.
+First they would take the short typing test three times to account for the three levels of music.
 

### 2024-04-18 typingTest/class.py
creates a file but adds commas

@@ -2,6 +2,7 @@
 import time
 import random
 import tkinter as tk
+from csv import *
 
 class gui(tk.Tk):
     def __init__(self):
@@ -37,6 +38,7 @@ class gui(tk.Tk):
         self.startTime = 0
         self.endTime = 0
         self.accuracy = 0
+        self.csv_file = []
 
         self.mainloop()
 
@@ -75,17 +77,39 @@ class gui(tk.Tk):
         self.accuracy = (sum(1 for x,y in zip(self.inputWords, self.inputFromUser) if x ==y) / self.totalWords) * 100
         if self.accuracy < 100:
             accuracyLabel = tk.Label(self, text = f'{self.accuracy:.3}% accuracy', font=('Arial', 20))
+            # accuracyText = "accuracy"
+            self.csv_file.append(accuracyLabel.cget("text"))
         else:
             accuracyLabel = tk.Label(self, text = f'{self.accuracy}% accuracy', font=('Arial', 20))
+            self.csv_file.append(accuracyLabel.cget("text"))
         accuracyLabel.pack()
         self.typingArea.destroy()
+        print(self.csv_file)
+        saveButton = tk.Button(self,text="Save", command=self.save())
+        saveButton.pack()
 
     def checkResults(self):
         self.endTime = time.time()
         self.done.destroy()
         timeLabel = tk.Label(self, text = f'Attempt took {time.strftime("%H:%M:%S", time.gmtime(self.endTime - self.startTime))}', font=('Arial', 20))
         timeLabel.pack()
+        self.csv_file.append(timeLabel.cget("text"))
         self.userAccuracy()
+
+    def save(self):
+        with open("file.txt","a") as file:
+            Writer=writer(file)
+            Writer.writerow(["accuracy","time"])
+            Writer.writerows(self.csv_file)
+            self.remove_commas()
+
+    def remove_commas(self):
+        with open("file.txt", "r") as file:
+            commas = file.readlines()
+        with open("file.txt", "w") as file:
+            for c in commas:
+                c.strip(",")
+                file.write(c)
 
 def main():
     one = gui()

### 2024-04-18 typingTest/class.py
tracks the time and accuracy

@@ -13,7 +13,7 @@ class gui(tk.Tk):
         self.maxsize(1500, 800)
         self.title("Typing Test")
         self.config(padx=50, pady=10)
-        self.instructions = tk.Label(wraplength=700, justify='center',font=('Arial', 14), text = "Type the prompt. The timer starts at the first keystroke. To end the typing portion, use the mouse to hit done. The QB test will then start.") 
+        self.instructions = tk.Label(wraplength=700, justify='center',font=('Arial', 14), text = "Type the prompt. The timer starts at the first keystroke. To end the typing portion, use the mouse to hit done.") 
         self.instructions.pack() # add the label to the window
 
         self.file = tk.Button(self, text = "Get the Typing Test", command=self.getFile)
@@ -77,15 +77,13 @@ class gui(tk.Tk):
         self.accuracy = (sum(1 for x,y in zip(self.inputWords, self.inputFromUser) if x ==y) / self.totalWords) * 100
         if self.accuracy < 100:
             accuracyLabel = tk.Label(self, text = f'{self.accuracy:.3}% accuracy', font=('Arial', 20))
-            # accuracyText = "accuracy"
             self.csv_file.append(accuracyLabel.cget("text"))
         else:
             accuracyLabel = tk.Label(self, text = f'{self.accuracy}% accuracy', font=('Arial', 20))
             self.csv_file.append(accuracyLabel.cget("text"))
         accuracyLabel.pack()
         self.typingArea.destroy()
-        print(self.csv_file)
-        saveButton = tk.Button(self,text="Save", command=self.save())
+        saveButton = tk.Label(self,text="Results Saved", font=('Arial', 20),  command=self.save())
         saveButton.pack()
 
     def checkResults(self):
@@ -98,22 +96,14 @@ class gui(tk.Tk):
 
     def save(self):
         with open("file.txt","a") as file:
-            Writer=writer(file)
-            Writer.writerow(["accuracy","time"])
-            Writer.writerows(self.csv_file)
-            self.remove_commas()
-
-    def remove_commas(self):
-        with open("file.txt", "r") as file:
-            commas = file.readlines()
-        with open("file.txt", "w") as file:
-            for c in commas:
-                c.strip(",")
-                file.write(c)
+            file.write("\n")
+            for item in self.csv_file:
+                help = item + " "
+                file.write(f'{help}')
+            file.write("\n")
 
 def main():
     one = gui()
-    # one.mainloop()
 
 if __name__ == '__main__':    
     main()

### 2024-04-18 typingTest/class.py
call class twice more

@@ -90,6 +90,8 @@ class gui(tk.Tk):
 def main():
     one = gui()
     # one.mainloop()
+    two = gui()
+    three = gui()
 
 if __name__ == '__main__':    
     main()

### 2024-04-18 typingTest/class.py
make full screen and center the txt box

@@ -7,12 +7,14 @@ class gui(tk.Tk):
     def __init__(self):
         super().__init__()
 
-        self.geometry("800x700+400+200") # Horizontal x Vertical
+        maxHeight = self.winfo_screenheight()
+        maxWidth = self.winfo_screenwidth()
+        self.geometry(f"{maxWidth}x{maxHeight}") # Horizontal x Vertical
         self.minsize(800, 700)
-        self.maxsize(1500, 800)
+
         self.title("Typing Test")
         self.config(padx=50, pady=10)
-        self.instructions = tk.Label(wraplength=700, justify='center',font=('Arial', 14), text = "Type the prompt. The timer starts at the first keystroke. To end the typing portion, use the mouse to hit done. The QB test will then start.") 
+        self.instructions = tk.Label(wraplength=700, justify='center',font=('Arial', 20), text = "Type the prompt. The timer starts at the first keystroke. To end the typing portion, use the mouse to hit done. The QB test will then start.") 
         self.instructions.pack() # add the label to the window
 
         self.file = tk.Button(self, text = "Get the Typing Test", command=self.getFile)
@@ -22,10 +24,13 @@ class gui(tk.Tk):
         # self.start.pack(side = "bottom", padx=10, pady=5)
 
         self.typingWindow = tk.Frame(width=200, height=40, padx=5, pady=5)
-        # self.typingWindow.place(x=100, y = 100)
-        self.typingWindow.pack(side = 'bottom')
+        # self.typingWindow.pack(side = 'bottom')
+        self.typingWindow.place(x=450, y = 300)
+        # self.typingWindow.pack(side = 'bottom')
+        # self.typingWindow.pack(expand=True)
+        # self.typingWindow.pack(fill='both')
 
-        self.typingArea = tk.Text(self.typingWindow, wrap='w', padx=5, pady=5, fg='black', bg='white', font='14')
+        self.typingArea = tk.Text(self.typingWindow, wrap='w', padx=5, pady=5, fg='black', bg='white', font='20')
         self.typingArea.pack()
 
         self.done = tk.Button(self, text='Done', command=self.checkResults)
@@ -58,7 +63,7 @@ class gui(tk.Tk):
             self.song = original
             self.inputWords = original.split()
             self.totalWords = len(self.inputWords)
-        label = tk.Label(self, text=original, font=('Arial', 14))
+        label = tk.Label(self, text=original, font=('Arial', 20))
         label.pack()
         self.file.destroy()
         self.userInput()

### 2024-04-19 qbTest/qb_test.py
Fullscreen and doesnt end

@@ -34,13 +34,14 @@ def save_score(score):
 
 # Main function to run the QB test
 def run_qb_test():
-    screen = pygame.display.set_mode((WIDTH, HEIGHT))
+    screen = pygame.display.set_mode((WIDTH, HEIGHT), pygame.FULLSCREEN)
     pygame.display.set_caption("QB Test - Press Space for Red")
     
     clock = pygame.time.Clock()
     font = pygame.font.Font(None, 36)
     running = False
     start_screen = True
+    game_ended = False
     last_flash_time = time.time()  # Track the last time a shape was flashed
     last_feedback_time = 0.0  # Track the last time feedback was displayed
     flash_complete = True  # Flag to track if a flash cycle is complete
@@ -137,6 +138,26 @@ def run_qb_test():
 
         pygame.display.flip()  # Update display
         clock.tick(FPS)  # Cap the frame rate
+
+    while game_ended:
+        screen.fill(WHITE)
+        display_text(screen, "QB Test", font, (0, 0, 0), (WIDTH // 2, HEIGHT // 4))
+        display_text(screen, "This test will exit on its own after 2 minutes.", font, (0, 0, 0), (WIDTH // 2, HEIGHT // 2 - 50))
+        display_text(screen, "Press Space to Start", font, (0, 0, 0), (WIDTH // 2, HEIGHT // 2 + 50))
+        for event in pygame.event.get():
+                if event.type == pygame.QUIT:
+                    game_ended = False
+                elif event.type == pygame.KEYDOWN:
+                    if event.key == pygame.K_SPACE:
+                        game_ended = False
+                        running = True
+                        start_time = time.time()
+                        score = 0
+                        break
+
+        pygame.display.flip()
+        clock.tick(FPS)
+
 
     pygame.quit()  # Clean up resources
 

### 2024-04-19 qbTest/qb_test.py
Stops after 3 tries

@@ -42,12 +42,16 @@ def run_qb_test():
     running = False
     start_screen = True
     game_ended = False
+    max_tries = 3
+    num_tries = 0
     last_flash_time = time.time()  # Track the last time a shape was flashed
     last_feedback_time = 0.0  # Track the last time feedback was displayed
     flash_complete = True  # Flag to track if a flash cycle is complete
     feedback_displayed = False  # Flag to track if feedback is currently displayed
     score = 0
     start_time = time.time()
+    turn_start_time = start_time  # Track the start time of each turn
+    
     
     while start_screen:
         screen.fill(WHITE)
@@ -63,6 +67,8 @@ def run_qb_test():
                 if event.key == pygame.K_SPACE:
                     start_screen = False
                     running = True
+                    num_tries = 0
+                    score = 0
                     break
 
         pygame.display.flip()
@@ -79,6 +85,14 @@ def run_qb_test():
         screen.fill(WHITE)
 
         current_time = time.time()
+
+        # Check if current turn has exceeded 2 minutes
+        if current_time - turn_start_time >= 120:
+            # End the current turn and reset for the next
+            num_tries = 0
+            score = 0
+            turn_start_time = current_time
+        
 
         if flash_complete:
             # Generate a random color for the shape
@@ -115,6 +129,7 @@ def run_qb_test():
                 running = False
             elif event.type == pygame.KEYDOWN:
                 if event.key == pygame.K_SPACE and not feedback_displayed:
+                    num_tries += 1
                     if current_color == RED:
                         feedback_message = "Correct!"
                         feedback_color = GREEN
@@ -125,6 +140,14 @@ def run_qb_test():
                     feedback_position = (WIDTH // 2, HEIGHT // 2 + SHAPE_RADIUS + 50)
                     last_feedback_time = current_time
                     feedback_displayed = True
+
+        if num_tries >= max_tries:
+            save_score(score)
+            display_text(screen, f"Correct: {score}", font, (0, 0, 0), (WIDTH // 2, HEIGHT // 2))
+            pygame.display.flip()
+            pygame.time.wait(2000)
+            running = False
+            game_ended = True        
 
         # Check for game end condition (e.g., after 2 mins)
         current_time = time.time()
@@ -151,6 +174,7 @@ def run_qb_test():
                     if event.key == pygame.K_SPACE:
                         game_ended = False
                         running = True
+                        num_tries = 0
                         start_time = time.time()
                         score = 0
                         break

### 2024-04-30 paper/paper.tex
qb test
add citations 6 & 7 to related works

--- 2024-03-31 paper/paper.tex
@@
 According to~\cite{Gonzalez_Aiello_2019}, the degree of cognitive function may be based on an individual's personality.
+The research done by Komlao found that music or background music was again based on an individual's personality but that music, even music that the participants were familiar with, were a distraction and ``was found to negatively impact task performace'' overall~\cite{komlao2018variations}.
+This was contrary to the previous studies found by Komlao where the ``music could help increase productivity for simple, monotonouse tasks''~\cite{komlao2018variations}.
 
@@
 The music was a detriment for logic puzzles in the user's accuracy but aided in the efficiency of a writing task.
+According to Bramwell-Dicks et el, the instrumental music used in their study had better results on typists in speed and accuracy whereas music with vocals, the participants fared worse~\cite{bramwell2016can}.
 

### 2024-04-30 paper/paper.tex
fix picture

--- 2024-04-17 paper/paper.tex
@@
 
-Participants were seated in a comfortable position facing the laptop screen.
-They were instructed to follow a series of calibration points displayed on the screen to calibrate the eye-tracking system.
-This calibration process ensured accurate measurement of eye movements during the subsequent tasks.
+Participants were seated in a comfortable position facing the laptop screen. The laptop is placed on top of a laptop stand while the eye tracker
+is mounted on a wooden frame. While the eye tracker is on a moveable slider, it is centered in front of the screen. At the ends of the wooden
+frame are infrared lights that flashes at sixty frames per second. % will need to verify that it is 60 fps.
+Although not pictured, a bluetooth keyboard is used by the participant for the quantified behavioral test (QB test).
 
-During the cognitive task component of the study, participants performed a quantified behavioral test (QBTest) while their eye movements were tracked by the EyeWriter 2.0 camera mounted on the laptop.
+\begin{figure}
+  \includegraphics[width=0.3\textwidth]{eyetracker_setup.png}
+  \caption{EyeWriter 2.0}
+  \Description{Image of the eye tracker setup}
+\end{figure}
+
+During the cognitive task component of the study, participants performed a QB test while their eye movements were tracked by the EyeWriter 2.0.
 The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
@@
 \subsection[short]{Participants}
-Approximately twenty participants were recruited from Colorado State University. Ten males and ten females all in the age range of 18-99. There were no %chktex 8
+Approximately eight participants were recruited from Colorado State University. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
 restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
@@
 
-\subsection[short]{Equipment}  % Do we want to change this to Equipment? 
+\subsection[short]{Equipment} 
 % This may not need to be broken into subsections. Will decide before we resubmit. 
@@
 One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it.
-The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test.
+The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test and QB test.
 
@@
 Participants used this MacBook Pro for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test.
+A bluetooth keyboard was used as part of the QB test since the positioning of the Eye Writer mostly blocked the space bar.
 
@@
 Cables are used to connect the IR camera and IR LEDs to the laptop. These cables transmit data and power between the components.
+An Arduino microcontroller allowed the computer to communicate with the camera, infrared LED lights, and computer.
 % \subsubsection{QB Test} 
@@
 First they would take the short typing test three times to account for the three levels of music.
+They would then do a QB test three times again for the music.
+The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.
 

### 2024-04-30 paper/paper.tex

@@
 While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
-studies that attempt to determine the answer. The other studies attempted to search for this answer by
-focusing on word processing on a computer with the background music and the user's ability to formulate sentences~\cite{ransdell2001141}, 
-or determining if background music helps users to keep their attention on their task at hand~\cite{kiss2021effect}.
-Similar to~\cite{kiss2021effect},~\cite{mathew2022inherently} also examined how motivation and music were used hand-in-hand on ``a time-consuming task and task performance''.
+studies that attempt to determine the answer. 
+The other studies attempted to search for this answer by focusing on word processing on a computer with the background music and the user's ability to formulate sentences~\cite{ransdell2001141}, or determining if background music helps users to keep their attention on their task at hand~\cite{kiss2021effect}.
+Similar to Kiss and Linnell~\cite{kiss2021effect}, Mathew ~\cite{mathew2022inherently} also examined how motivation and music were used hand-in-hand on ``a time-consuming task and task performance''. 
 A different study done in 2010 again found similar results of music both being a hindrance and benefit~\cite{AudioDistractionsAshley}. 
-According to~\cite{Gonzalez_Aiello_2019}, the degree of cognitive function may be based on an individual's personality.
+According to Gonzalez and Aiello~\cite{Gonzalez_Aiello_2019}, the degree of cognitive function may be based on an individual's personality. 
+Furnham et al., also determined this was based on personality in a study done between extraverts and introverts although ``no significant interactions were found''~\cite{distractingEffectsFurnham}.
 
-Although~\cite{ransdell2001141} suggests that the music is a detriment, those with ``musical training and high working memory span wrote better essays with longer sentences'.
+The research done by Komlao found that music or background music was again based on an individual's personality but that music, even music that the participants were familiar with, were a distraction and ``was found to negatively impact task performace'' overall~\cite{komlao2018variations}.
+This was contrary to the previous studies found by Komlao where the ``music could help increase productivity for simple, monotonouse tasks''~\cite{komlao2018variations}.
+
+Although Ransdell and Gilroy~\cite{ransdell2001141} suggests that the music is a detriment, those with ``musical training and high working memory span wrote better essays with longer sentences''. 
 This suggests that while the music slowed down the participants, it did not necessarily lower their cognitive ability in typing on their computer while focusing on forming text for the written essay for this particular study.
-For~\cite{AudioDistractionsAshley}, the music caused enough of a difference in the time that was taken for writing a paragraph but ``there were no significant differences in typing speed between the audio distractions''.
+For Silverberg~\cite{AudioDistractionsAshley}, the music caused enough of a difference in the time that was taken for writing a paragraph but ``there were no significant differences in typing speed between the audio distractions''.
 This again may suggest that the participant's cognitive ability was not hindered when typing and may transfer directly after should the participants have taken a test measuring their cognitive function.
-The slow timing was again seen in~\cite{Gonzalez_Aiello_2019} in which ``music generally impaired performance on a complex task but improved performance on a simple task''.
+The slow timing was again seen by Gonzalez and Aiello~\cite{Gonzalez_Aiello_2019} in which ``music generally impaired performance on a complex task but improved performance on a simple task''.
 
-The study done through~\cite{kiss2021effect} saw opposite results as to~\cite{Gonzalez_Aiello_2019}.
+The study done through Kiss and Linnell~\cite{kiss2021effect} saw opposite results as to Gonzalez and Aiello~\cite{Gonzalez_Aiello_2019}.
 The music or background noise ``enhanced'' the reaction time and performance of the tasks that are given to be completed.
-The results from~\cite{mathew2022inherently} were split.
+The results from Mathew~\cite{mathew2022inherently} were split. 
 The music was a detriment for logic puzzles in the user's accuracy but aided in the efficiency of a writing task. 
+According to Bramwell-Dicks et al., the instrumental music used in their study had better results on typists in speed and accuracy whereas music with vocals, the participants fared worse~\cite{bramwell2016can}.
+While only a quasi-experiment, Oldham et al., found that personal headphones and Walkmans for employees had a postive correlation if the job complexity was not complex but also that employee satisfaction at this company was higher if they were allowed to use their walkman while working~\cite{oldhamListen}.
+Dobbs et al., also found the correlation that while music produced lower scores than silence it was better than just ``noise''~\cite{effectsOfBackgroundDobbs}.
 

### 2024-04-30 paper/paper.tex
being anal about formatting

@@
 The Quantified Behavioral Test (QBTest) is a well-established tool for assessing cognitive function, particularly in measuring hand-eye coordination, speed, and accuracy.
-Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions.
-% This would be a good place to put a citation.
+Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions. % This would be a good place to put a citation.
 In this study, the QBTest serves as a central component for evaluating participants' cognitive response time and typing efficiency under various music conditions.
@@
 After they hit the ``Get the Typing Test'' button, the lyrics of the randomly selected songs were displayed for the user to type. 
-The text box for the users was already in focus with a ``Done'' button.
-After the users hit ``Done'', their accuracy and speed were presented.
+The text box for the users was already in focus with a ``Done'' button. After the users hit ``Done'', their accuracy and speed were presented.
+
+% START REWRITING HERE
 
@@
 
-Participants were seated in a comfortable position facing the laptop screen. The laptop is placed on top of a laptop stand while the eye tracker
-is mounted on a wooden frame. While the eye tracker is on a moveable slider, it is centered in front of the screen. At the ends of the wooden
-frame are infrared lights that flashes at sixty frames per second. % will need to verify that it is 60 fps.
-Although not pictured, a bluetooth keyboard is used by the participant for the quantified behavioral test (QB test).
+Participants were seated in a comfortable position facing the laptop screen.
+The laptop is placed on top of a laptop stand while the eye tracker is mounted on a wooden frame. 
+While the eye tracker is on a moveable slider, it is centered in front of the screen. 
+At the ends of the wooden frame are infrared lights that flashes at sixty frames per second. % will need to verify that it is 60 fps.
+Although not pictured, a bluetooth keyboard is used by the participant for the quantified behavioral test (QBTest).
 
@@
 
-During the cognitive task component of the study, participants performed a QB test while their eye movements were tracked by the EyeWriter 2.0.
+During the cognitive task component of the study, participants performed a Quantified Behavioral test or QBTest while their eye movements were tracked by the EyeWriter 2.0.
 The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
@@
 One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it.
-The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test and QB test.
+The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test and QBTest.
 
@@
 Participants used this MacBook Pro for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test.
-A bluetooth keyboard was used as part of the QB test since the positioning of the Eye Writer mostly blocked the space bar.
+A bluetooth keyboard was used as part of the QBTest since the positioning of the Eye Writer mostly blocked the space bar.
 
@@
 An Arduino microcontroller allowed the computer to communicate with the camera, infrared LED lights, and computer.
-% \subsubsection{QB Test} 
+
 \subsubsection{Typing Test}
@@
 \subsubsection{Quantified Behavioral Test}
-The Quantified Behavioral Test or QBTest program was written in Python and compiled using Python3.9.
+The Quantified Behavioral Test program was written in Python and compiled using Python3.9.
 The package pygame was used for this interface compared to the package tkinter used for the typing test.
+The bluetooth keyboard allowed the participant to hit the space bar when the QBTest said to hit the space bar.
 
 \subsection[short]{Procedure}
-After signing consent forms, each participant was explained the overall concept of what they would be doing.
+Each participant was instructed to read and then sign the consent form.
+While the consent form had the basis of what they would be doing, they were given more detail as to the instructions when they were ready to begin.
+ %REWRITE THIS HERE
 First they would take the short typing test three times to account for the three levels of music. 
-They would then do a QB test three times again for the music.
-The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.
+They would then do a QBTest three times again for the music. The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.
 

### 2024-05-01 Latex Source/paper.tex

--- 2024-04-30 paper/paper.tex
@@
 
-Participants were seated in a comfortable position facing the laptop screen. The laptop is placed on top of a laptop stand while the eye tracker
-is mounted on a wooden frame. While the eye tracker is on a moveable slider, it is centered in front of the screen. At the ends of the wooden
-frame are infrared lights that flashes at sixty frames per second. % will need to verify that it is 60 fps.
-Although not pictured, a bluetooth keyboard is used by the participant for the quantified behavioral test (QB test).
+Participants were seated in a comfortable position facing the laptop screen.
+They were instructed to follow a series of calibration points displayed on the screen to calibrate the eye-tracking system.
+This calibration process ensured accurate measurement of eye movements during the subsequent tasks.
 
-\begin{figure}
-  \includegraphics[width=0.3\textwidth]{eyetracker_setup.png}
-  \caption{EyeWriter 2.0}
-  \Description{Image of the eye tracker setup}
-\end{figure}
-
-During the cognitive task component of the study, participants performed a QB test while their eye movements were tracked by the EyeWriter 2.0.
+During the cognitive task component of the study, participants performed a quantified behavioral test (QBTest) while their eye movements were tracked by the EyeWriter 2.0 camera mounted on the laptop.
 The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
@@
 \subsection[short]{Participants}
-Approximately eight participants were recruited from Colorado State University. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
+Approximately twenty participants were recruited from Colorado State University. Ten males and ten females all in the age range of 18-99. There were no %chktex 8
 restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
@@
 
-\subsection[short]{Equipment} 
+\subsection[short]{Apparatus}  % Do we want to change this to Equipment? 
 % This may not need to be broken into subsections. Will decide before we resubmit. 
-Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 14.
+Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 1.
 One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it.
-The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test and QB test.
+The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test.
 
@@
 Participants used this MacBook Pro for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test.
-A bluetooth keyboard was used as part of the QB test since the positioning of the Eye Writer mostly blocked the space bar.
 
@@
 Cables are used to connect the IR camera and IR LEDs to the laptop. These cables transmit data and power between the components.
-An Arduino microcontroller allowed the computer to communicate with the camera, infrared LED lights, and computer.
 % \subsubsection{QB Test} 
@@
 
-\subsubsection{Quantified Behavioral Test}
-The Quantified Behavioral Test or QBTest program was written in Python and compiled using Python3.9.
-The package pygame was used for this interface compared to the package tkinter used for the typing test.
-
 \subsection[short]{Procedure}
-After signing consent forms, each participant was explained the overall concept of what they would be doing.
-First they would take the short typing test three times to account for the three levels of music.
-They would then do a QB test three times again for the music.
-The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.
+Procedure
 
@@
 \section{Results and Discussion}
-Within-subjects testing was used.
+Results and Discussion
 

### 2024-05-01 Latex Source/paper.tex

--- 2024-04-30 paper/paper.tex
@@
 \documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
-% \documentclass was [sigconf]{acmart} changed to match with the given overleaf link
 % \documentclass[sigconf]{acmart}
@@
 \author{Shea Spalding}
-\email{Shea1@colostate.edu} %update email 
+\email{Shea1@colostate.edu}
 \affiliation{%
@@
 \section{Related Works}
+\subsection{Music While Working}
 While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
@@
 
+\subsection{Eye Tracking and Quantified Behavioral Test}
+% Citations about eye tracking and QBTest here
+
 \section{Methodology}
 After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
-The interface automatically calculated typing speed and accuracy in the program's backend, allowing participants to focus solely on completing the test.
+The interface automatically calculated typing accuracy and the time the attempt took in the program's backend, allowing participants to focus solely on completing the test.
 Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
@@
 
-% START REWRITING HERE
-
 Following the typing test, participants proceeded to the cognitive task component of the study, which was also conducted under the three aforementioned conditions. 
@@
 \subsection[short]{Participants}
-Approximately eight participants were recruited from Colorado State University. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
+Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
 restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
@@
  %REWRITE THIS HERE
-First they would take the short typing test three times to account for the three levels of music. 
-They would then do a QBTest three times again for the music. The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.
+%First they would take the short typing test three times to account for the three levels of music. 
+%They would then do a QBTest three times again for the music. 
+%The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.
+The two computers were set up side by side so that it would be easy for the participant to switch between the typing test and QBTest.
+This setup also made it simple for the music component as the participants did each level together (e.g. the no music level was typing test 
+then the QBTest) before moving on to the next level.
 

### 2024-05-02 Latex Source/paper.tex
start design portion

@@
 The two computers were set up side by side so that it would be easy for the participant to switch between the typing test and QBTest.
-This setup also made it simple for the music component as the participants did each level together (e.g. the no music level was typing test 
-then the QBTest) before moving on to the next level.
+This setup also made it simple for the music component as the participants did each level together 
+(e.g. typing test then QBTest without having to change the music or swapping to no music)
+before moving on to the next level. 
+Because of the way that the heatmap was coded, we had to make sure that each level was done in the same order for all the participants.
+We made sure to always do instrumental music, lyrical music, then no music.
 

### 2024-05-02 Latex Source/paper.tex
change typing images

@@
 \subsection{Eye Tracking and Quantified Behavioral Test}
-% Citations about eye tracking and QBTest here
+Citations about eye tracking and QBTest here
 
@@
 
-\begin{figure}
-  \includegraphics[width=0.3\textwidth]{typing_test_1}
-  \caption{Starting window of typing test}
-  \Description{Image of the starting windows of the typing test}
-\end{figure}
+% \begin{figure}
+%   \includegraphics[width=0.3\textwidth]{typing_test_1}
+%   \caption{Starting window of typing test}
+%   \Description{Image of the starting windows of the typing test}
+% \end{figure}
+
+% \begin{figure}
+%   \includegraphics[width=0.3\textwidth]{typing_test_2}
+%   \caption{Test started}
+%   \Description{Image of the test with the lyrics that the user will type}
+% \end{figure}
+
+% \begin{figure}
+%   \includegraphics[width=0.3\textwidth]{typing_test_3}
+%   \caption{Test finished}
+%   \Description{Image of the finished test}
+% \end{figure}
 
 \begin{figure}
-  \includegraphics[width=0.3\textwidth]{typing_test_2}
-  \caption{Test started}
-  \Description{Image of the test with the lyrics that the user will type}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=0.3\textwidth]{typing_test_3}
-  \caption{Test finished}
-  \Description{Image of the finished test}
+  \includegraphics[width=\textwidth]{typingTest}
+  \caption{Typing Test Screenshots}
+  \Description{Images of what the user will see in the typing test}
 \end{figure}
@@
 % Further details on the cognitive task will be provided in subsequent sections. They will then move on the the QBTest?. % This will need to be re-written.
-
-\subsection[short]{Participants}
-Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
-restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
-They have all previously either learned to type at primary school or through necessity.
 
@@
 
-\subsection[short]{Design}
-Design
+\subsection[short]{Participants and Design}
+Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
+restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
+They have all previously either learned to type at primary school or through necessity.
 

### 2024-05-04 Latex Source/paper.tex
add music credits for songs w/lyrics and update gitignore

@@
 
-% \begin{figure}
-%   \includegraphics[width=0.3\textwidth]{typing_test_1}
-%   \caption{Starting window of typing test}
-%   \Description{Image of the starting windows of the typing test}
-% \end{figure}
-
-% \begin{figure}
-%   \includegraphics[width=0.3\textwidth]{typing_test_2}
-%   \caption{Test started}
-%   \Description{Image of the test with the lyrics that the user will type}
-% \end{figure}
-
-% \begin{figure}
-%   \includegraphics[width=0.3\textwidth]{typing_test_3}
-%   \caption{Test finished}
-%   \Description{Image of the finished test}
-% \end{figure}
-
 \begin{figure}
   \includegraphics[width=\textwidth]{typingTest}
-  \caption{Typing Test Screenshots}
+  \caption{Images of what the user will see in the typing test}
   \Description{Images of what the user will see in the typing test}
@@
 \begin{figure}
-  \includegraphics[width=0.3\textwidth]{eyetracker_setup.png}
-  \caption{EyeWriter 2.0}
+  \includegraphics[width=0.5\textwidth]{eyetracker_setup.png}
+  \caption{EyeWriter 2.0 Setup}
   \Description{Image of the eye tracker setup}
@@
 The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
+
+\begin{figure}
+  \includegraphics[width=\textwidth]{qbTest.png}
+  \caption{Images of what the user will see in the QBTest}
+  \Description{Images of what the user will see in the QBTest}
+\end{figure}
+
 % Further details on the cognitive task will be provided in subsequent sections. They will then move on the the QBTest?. % This will need to be re-written.
@@
 \subsection[short]{Participants and Design}
-Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
-restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
+Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado.
+Two males and eight females all in the age range of 18-23.
+There were no restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
 They have all previously either learned to type at primary school or through necessity.
@@
 
-\section{Conclusion}
+\section{Conclusion and Future Works}
 Conclusion

### 2024-05-04 Latex Source/paper.tex
finished design

@@
 
+% part of the template 
 \AtBeginDocument{%
@@
 
-\usepackage{etoolbox} 
-\apptocmd{\sloppy}{\hbadness 10000\relax} {}{} %chktex 1
-
-\usepackage[skip=6pt plus1pt]{parskip} %% add space between the paragraphs
-
-\usepackage{graphicx} %% For pictures
-\graphicspath{{./pics/}}
-\usepackage[section]{placeins} %% used to keep the images in the section that I want them in
-
+% part of the template 
 \setcopyright{acmcopyright}
@@
 \acmDOI{XXXXXXX.XXXXXXX}
+
+% packages that I added
+\usepackage{graphicx} %% For pictures
+\graphicspath{{./pics/}}
+\usepackage[section]{placeins} %% used to keep the images in the section that I want them in
 
@@
 
-\ccsdesc{Music, Typing Efficiency} % Update this
-\keywords{Typing Efficiency with Music, Cognitive Function} % placeholder text for the time being
+\ccsdesc{Music, Typing Efficiency, Cognitive Function}
+\keywords{Typing Efficiency with Music, Cognitive Function, Quantified Behavioral Test}
 \maketitle
@@
 \subsection{Eye Tracking and Quantified Behavioral Test}
-Citations about eye tracking and QBTest here
+
+CITATIONS ABOUT EYE TRACKING AND QBTEST HERE
 
 \section{Methodology}
+\subsection[short]{Equipment} 
+Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 14.
+One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it.
+The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test and QBTest.
+Participants used the MacBook Pro with the eye tracker for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test. 
+A bluetooth keyboard allowed participants to press the space bar in the Quantified Behavioral test easily as the mounting of the eye tracker made it harder to access
+the space bar on the MacBook.
+Using two separate MacBook Pros allowed for the independent administration of the QBTest and typing test, ensuring that participants could perform each task without any physical hindrance from the eye tracker.
+
+\subsubsection{EyeWriter 2.0}
+The IR camera captures the eye movements of the participant.
+It is mounted on the laptop that participants use for the QBTest, allowing for the tracking of eye movements during the test.
+IR LEDs are used to illuminate the eye to enhance the visibility of the eye for tracking purposes. 
+These LEDs are also mounted on the laptop along with the IR camera. 
+The mounting system holds the IR camera and IR LEDs in place relative to the participant's eye. 
+It ensures that the camera has a clear view of the eye for accurate tracking. 
+Cables are used to connect the IR camera and IR LEDs to the laptop. These cables transmit data and power between the components.
+An Arduino microcontroller allowed the computer to communicate with the camera, infrared LED lights, and computer.
+
+\subsubsection{Typing Test}
+The typing program was written in Python and compiled using Python3.9. 
+While python can run on any device that has python installed, this study only used the two Macbook Pros. 
+The singularity of the devices was used as the center of the screen for the typing test was hard coded when setting the starting position of the window for the typing test.
+
+\subsubsection{Quantified Behavioral Test}
+The Quantified Behavioral Test program was written in Python and compiled using Python3.9.
+The package pygame was used for this interface compared to the package tkinter used for the typing test.
+The bluetooth keyboard allowed the participant to hit the space bar when the QBTest said to hit the space bar.
+
+\subsection[short]{Procedure}
+Each participant was instructed to read and then sign the consent form.
+While the consent form had the basis of what they would be doing, they were given more detail as to the instructions when they were ready to begin.
+The two computers were set up side by side so that it would be easy for the participant to switch between the typing test and QBTest.
+This setup also made it simple for the music component as the participants did each level together 
+(e.g. typing test then QBTest without having to change the music or swapping to no music)
+before moving on to the next level. 
+Because of the way that the heatmap was coded, we had to make sure that each level was done in the same order for all the participants.
+We made sure to always do instrumental music, lyrical music, then no music.
+
+\subsection[short]{Participants}
+Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado.
+Two males and eight females all in the age range of 18-23.
+There were no restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
+They have all previously either learned to type at primary school or through necessity.
+
+\subsection[short]{Design}
 After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
@@
 While the eye tracker is on a moveable slider, it is centered in front of the screen. 
-At the ends of the wooden frame are infrared lights that flashes at sixty frames per second. % will need to verify that it is 60 fps.
+At the ends of the wooden frame are infrared lights that flashes at sixty frames per second. % WILL NEED TO VERIFY THAT IT IS 60 FPS
 Although not pictured, a bluetooth keyboard is used by the participant for the quantified behavioral test (QBTest).
@@
 
-% Further details on the cognitive task will be provided in subsequent sections. They will then move on the the QBTest?. % This will need to be re-written.
-
-\subsection[short]{Equipment} 
-% This may not need to be broken into subsections. Will decide before we resubmit. 
-Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 14.
-One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it.
-The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test and QBTest.
-
-QBTest MacBook Pro with Eye Tracker: This MacBook Pro was dedicated to conducting the QBTest.
-It had the eye tracker mounted on it, which made it difficult to access the keyboard for typing.
-Participants used this MacBook Pro for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test.
-A bluetooth keyboard was used as part of the QBTest since the positioning of the Eye Writer mostly blocked the space bar.
-
-Typing Test MacBook Pro: The second MacBook Pro was used for the typing test.
-Since it did not have the eye tracker mounted on it, participants could easily access the keyboard and perform the typing test without any interference from the eye tracker.
-Using two separate MacBook Pros allowed for the independent administration of the QBTest and typing test, ensuring that participants could perform each task without any physical hindrance from the eye tracker.
-
-\subsubsection{EyeWriter 2.0}
-The IR camera captures the eye movements of the participant.
-It is mounted on the laptop that participants use for the QBTest, allowing for the tracking of eye movements during the test.
-IR LEDs are used to illuminate the eye to enhance the visibility of the eye for tracking purposes. 
-These LEDs are also mounted on the laptop along with the IR camera. 
-The mounting system holds the IR camera and IR LEDs in place relative to the participant's eye. 
-It ensures that the camera has a clear view of the eye for accurate tracking. 
-Cables are used to connect the IR camera and IR LEDs to the laptop. These cables transmit data and power between the components.
-An Arduino microcontroller allowed the computer to communicate with the camera, infrared LED lights, and computer.
-
-\subsubsection{Typing Test}
-The typing program was written in Python and compiled using Python3.9. 
-While python can run on any device that has python installed, this study only used the two Macbook Pros. 
-The singularity of the devices was used as the center of the screen for the typing test was hard coded when setting the starting position of the window for the typing test.
-
-\subsubsection{Quantified Behavioral Test}
-The Quantified Behavioral Test program was written in Python and compiled using Python3.9.
-The package pygame was used for this interface compared to the package tkinter used for the typing test.
-The bluetooth keyboard allowed the participant to hit the space bar when the QBTest said to hit the space bar.
-
-\subsection[short]{Procedure}
-Each participant was instructed to read and then sign the consent form.
-While the consent form had the basis of what they would be doing, they were given more detail as to the instructions when they were ready to begin.
- %REWRITE THIS HERE
-%First they would take the short typing test three times to account for the three levels of music. 
-%They would then do a QBTest three times again for the music. 
-%The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.
-The two computers were set up side by side so that it would be easy for the participant to switch between the typing test and QBTest.
-This setup also made it simple for the music component as the participants did each level together 
-(e.g. typing test then QBTest without having to change the music or swapping to no music)
-before moving on to the next level. 
-Because of the way that the heatmap was coded, we had to make sure that each level was done in the same order for all the participants.
-We made sure to always do instrumental music, lyrical music, then no music.
-
-\subsection[short]{Participants and Design}
-Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado.
-Two males and eight females all in the age range of 18-23.
-There were no restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
-They have all previously either learned to type at primary school or through necessity.
-
 \section{Results and Discussion}

### 2024-05-04 Latex Source/paper.tex
fix images

@@
 The GUI of the typing test was built with simplicity in mind.
-The starting window was pulled up so as not to confuse participants with the code as seen in Figure 1.
-The participants saw Figure 2 while the test is running, while Figure 3 is the signifier that the typing portion is finished.
+The starting window was pulled up so as not to confuse participants with the code as seen in Figure 1a.
+The participants saw Figure 1b while the test is running, while Figure 1c is the signifier that the typing portion is finished.
 
@@
 The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
+% MAYBE ADD MORE ABOUT THE QBTEST?
 

### 2024-05-06 Latex Source/paper.tex
add labels to figures

@@
 The GUI of the typing test was built with simplicity in mind.
-The starting window was pulled up so as not to confuse participants with the code as seen in Figure 1a.
-The participants saw Figure 1b while the test is running, while Figure 1c is the signifier that the typing portion is finished.
+The starting window was pulled up so as not to confuse participants with the code as seen in Figure \ref*{typingTest} (a).
+The participants saw Figure \ref*{typingTest} (b) while the test is running, while Figure \ref*{typingTest} (c) is the signifier that the typing portion is finished.
 
@@
   \Description{Images of what the user will see in the typing test}
+  \label{typingTest}
 \end{figure}
@@
 The EyeWriter system consists of a camera mounted on the participant's laptop, which tracks eye movements and allows for precise measurement of gaze direction and fixation duration.
+This can be seen in Figure \ref{EyeWriter}.
 
@@
   \Description{Image of the eye tracker setup}
+  \label{EyeWriter}
 \end{figure}
@@
 The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
+The user will then see Figure \ref*{QBTest}.
 % MAYBE ADD MORE ABOUT THE QBTEST?
@@
   \Description{Images of what the user will see in the QBTest}
+  \label{QBTest}
 \end{figure}
@@
 \section{Results and Discussion}
-Within-subjects testing was used.
+Within-subjects testing was used for our ten participants. Individually the typing test and QBTest scores were not statistically significant, whereas 
+% WHATEVER TYPE OF TESTING IS USED (ANOVA)
+the ANOVA from the heatmap with the eyetracker, the results were statistically significant. %sounds clunky might change
+The ANOVA for the typing test was done twice for the dependent variables, time and accuracy, as GoStats did not allow for multiple 
+dependent variables. Both were not statistically significant although their \textit{p} values were different.
 

### 2024-05-06 Latex Source/paper.tex

--- 2024-05-04 Latex Source/paper.tex
@@
 The two-part test aims to help test if the music is too distracting or will help the people be more efficient at their work. 
-This is important because many people do their homework or jobs while listening to music and should they make a mistake, it could end up costing someone their grade or the mistake at work has a cascading effect to cause more errors in their work.
+This is important because many people do their homework or jobs while listening to music and should they make a mistake, it could end up costing someone their grade or the mistake at work has a cascading effect to cause more errors.
+According to the arousal-mood hypothesis, changes in arousal and mood when exposed to auditory stimulation can influence cognitive function \cite{Chee}.
 The two-part test will help determine if there is a correlation between the effectiveness of music versus no music on cognitive response time and typing efficiency.
@@
 \subsection{Eye Tracking}
-Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements. 
+Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements \cite{Rana8642988}.
 In this study, we incorporate the EyeWriter 2.0 to track participants' eye movements during the QBTest, a hand-eye coordination task.
-The EyeWriter 2.0 offers high-resolution tracking, capturing gaze patterns and fixations with accuracy. 
-By analyzing participants' eye movements during the QBTest under different music conditions, we aim to understand how distractions, such as music, influence visual attention and cognitive performance.
+The EyeWriter 2.0 offers high-resolution tracking, accurately capturing gaze patterns and fixations.
+As Chen \cite{Chen23876} points out while exploring the relationships between distractibility and Eye Tracking during online learning assessments they found significant differences between more distractions meant more distracted eyes.
+We believe by analyzing participants' eye movements during the QBTest under different music conditions, we aim to understand how distractions, such as music, influence visual attention and cognitive performance.
 Understanding the impact of music on cognitive response time and typing efficiency, as measured by the QBTest and eye tracking, can provide valuable insights for improving work and study environments where music is commonly used as a background stimulus.
@@
 The Quantified Behavioral Test (QBTest) is a well-established tool for assessing cognitive function, particularly in measuring hand-eye coordination, speed, and accuracy.
-Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions. % This would be a good place to put a citation.
+It is usually used to diagnose ADHD in adults and children as mentioned by \cite{Stevanovic} Stevanovic in their study of 'The Structure and Diagnostic Accuracy of the QbTest in Pediatric ADHD.
+Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions.
 In this study, the QBTest serves as a central component for evaluating participants' cognitive response time and typing efficiency under various music conditions.
 By administering the QBTest alongside eye tracking using EyeWriter 2.0, we aim to understand the impact of music on cognitive function and task performance.
-The QBTest's ability to quantify cognitive performance makes it an ideal tool for this study, allowing us to measure the effects of music on participants' ability to focus, process information, and perform tasks accurately.
+The QBTest's ability to quantify cognitive performance makes it an ideal tool for this study, allowing us to measure the effects of music on participants' ability to focus, process information, and perform tasks fairly accurately.
+It is also important to understand that it is not completely accurate as discussed by Hult \cite{Hult}.
 Through this research, we seek to provide insights that can enhance our understanding of how environmental factors, such as music, influence cognitive processes.
@@
 Typing proficiency is a fundamental skill in today's digital age, essential for academic and professional success. 
-However, various factors can influence typing efficiency, including environmental stimuli such as music.
+However, various factors can influence typing efficiency, including environmental stimuli such as music Silverberg \cite{AudioDistractionsAshley} found that the results of their typing test showed that although there was a significant difference in the times between paragraphs, there were no significant differences in typing speed between the audio distractions being played.
 Understanding how music affects typing speed and accuracy is crucial for optimizing work and study environments.
@@
 According to Bramwell-Dicks et al., the instrumental music used in their study had better results on typists in speed and accuracy whereas music with vocals, the participants fared worse~\cite{bramwell2016can}.
-While only a quasi-experiment, Oldham et al., found that personal headphones and Walkmans for employees had a postive correlation if the job complexity was not complex but also that employee satisfaction at this company was higher if they were allowed to use their walkman while working~\cite{oldhamListen}.
+While only a quasi-experiment, Oldham et al., found that personal headphones and Walkmans for employees had a positive correlation if the job complexity was not complex but also that employee satisfaction at this company was higher if they were allowed to use their walkman while working~\cite{oldhamListen}.
 Dobbs et al., also found the correlation that while music produced lower scores than silence it was better than just ``noise''~\cite{effectsOfBackgroundDobbs}.
@@
 The package pygame was used for this interface compared to the package tkinter used for the typing test.
-The bluetooth keyboard allowed the participant to hit the space bar when the QBTest said to hit the space bar.
+The Bluetooth keyboard allowed the participant to hit the space bar when the QBTest said to hit the space bar.
 
@@
 Because of the way that the heatmap was coded, we had to make sure that each level was done in the same order for all the participants.
-We made sure to always do instrumental music, lyrical music, then no music.
+We made sure to always do instrumental music, lyrical music, and then no music.
 
 \subsection[short]{Participants}
-Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado.
+Twelve participants were recruited from Colorado State University or Fort Collins, Colorado.
 Two males and eight females all in the age range of 18-23.
@@
 The starting window was pulled up so as not to confuse participants with the code as seen in Figure 1.
-The participants saw Figure 2 while the test is running, while Figure 3 is the signifier that the typing portion is finished.
+The participants saw Figure 2 while the test was running, while Figure 3 was the signifier that the typing portion was finished.
 
@@
 While the eye tracker is on a moveable slider, it is centered in front of the screen. 
-At the ends of the wooden frame are infrared lights that flashes at sixty frames per second. % WILL NEED TO VERIFY THAT IT IS 60 FPS
+At the ends of the wooden frame are infrared lights that flash at sixty frames per second. % WILL NEED TO VERIFY THAT IT IS 60 FPS
 Although not pictured, a bluetooth keyboard is used by the participant for the quantified behavioral test (QBTest).

### 2024-05-06 Latex Source/paper.tex
fix references to figures

--- 2024-05-06 Latex Source/paper.tex
@@
 The GUI of the typing test was built with simplicity in mind.
-The starting window was pulled up so as not to confuse participants with the code as seen in Figure \ref*{typingTest} (a).
-The participants saw Figure \ref*{typingTest} (b) while the test is running, while Figure \ref*{typingTest} (c) is the signifier that the typing portion is finished.
+The starting window was pulled up so as not to confuse participants with the code as seen in Figure \ref*{typingTest}a.
+The participants saw Figure \ref*{typingTest}b while the test is running, while Figure \ref*{typingTest}c is the signifier that the typing portion is finished.
 
@@
 The EyeWriter system consists of a camera mounted on the participant's laptop, which tracks eye movements and allows for precise measurement of gaze direction and fixation duration.
-This can be seen in Figure \ref{EyeWriter}.
+This can be seen in Figure \ref*{EyeWriter}.
 
@@
 The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
-The user will then see Figure \ref*{QBTest}.
+The user will then see Figure \ref*{QBTest}. Figure \ref*{QBTest}a is the screen that will be displayed before the participant is ready to begin the QBTest.
+Figure \ref*{QBTest}b is what the user will see during the test. Figure \ref*{QBTest}b also displays what the user will see when they are correct and incorrect.
+Figure \ref*{QBTest}c displays for only two minutes but shows the user their score.
 % MAYBE ADD MORE ABOUT THE QBTEST?

### 2024-05-06 Latex Source/paper.tex

--- 2024-05-06 Latex Source/paper.tex
@@
 The GUI of the typing test was built with simplicity in mind.
-The starting window was pulled up so as not to confuse participants with the code as seen in Figure 1.
-The participants saw Figure 2 while the test was running, while Figure 3 was the signifier that the typing portion was finished.
+The starting window was pulled up so as not to confuse participants with the code as seen in Figure \ref*{typingTest}a.
+The participants saw Figure \ref*{typingTest}b while the test was running, while Figure \ref*{typingTest}c was the signifier that the typing portion was finished.
 
@@
 The EyeWriter system consists of a camera mounted on the participant's laptop, which tracks eye movements and allows for precise measurement of gaze direction and fixation duration.
+This can be seen in Figure \ref*{EyeWriter}.
 
@@
 The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
+The user will then see Figure \ref*{QBTest}. Figure \ref*{QBTest}a is the screen that will be displayed before the participant is ready to begin the QBTest.
+Figure \ref*{QBTest}b is what the user will see during the test. Figure \ref*{QBTest}b also displays what the user will see when they are correct and incorrect.
+Figure \ref*{QBTest}c displays for only two minutes but shows the user their score.
+% MAYBE ADD MORE ABOUT THE QBTEST?
 

### 2024-05-06 Latex Source/paper.tex
compiler got mad at citations

@@
 This is important because many people do their homework or jobs while listening to music and should they make a mistake, it could end up costing someone their grade or the mistake at work has a cascading effect to cause more errors.
-According to the arousal-mood hypothesis, changes in arousal and mood when exposed to auditory stimulation can influence cognitive function \cite{Chee}.
+According to the arousal-mood hypothesis, changes in arousal and mood when exposed to auditory stimulation can influence cognitive function~\cite{Chee}.
 The two-part test will help determine if there is a correlation between the effectiveness of music versus no music on cognitive response time and typing efficiency.
@@
 \subsection{Eye Tracking}
-Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements \cite{Rana8642988}.
+Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements~\cite{Rana8642988}.
 In this study, we incorporate the EyeWriter 2.0 to track participants' eye movements during the QBTest, a hand-eye coordination task.
 The EyeWriter 2.0 offers high-resolution tracking, accurately capturing gaze patterns and fixations.
-As Chen \cite{Chen23876} points out while exploring the relationships between distractibility and Eye Tracking during online learning assessments they found significant differences between more distractions meant more distracted eyes.
+As Chen~\cite{Chen23876} points out while exploring the relationships between distractibility and Eye Tracking during online learning assessments they found significant differences between more distractions meant more distracted eyes.
 We believe by analyzing participants' eye movements during the QBTest under different music conditions, we aim to understand how distractions, such as music, influence visual attention and cognitive performance.
@@
 The Quantified Behavioral Test (QBTest) is a well-established tool for assessing cognitive function, particularly in measuring hand-eye coordination, speed, and accuracy. 
-It is usually used to diagnose ADHD in adults and children as mentioned by \cite{Stevanovic} Stevanovic in their study of 'The Structure and Diagnostic Accuracy of the QbTest in Pediatric ADHD.
+It is usually used to diagnose ADHD in adults and children as mentioned by~\cite{Stevanovic} Stevanovic in their study of 'The Structure and Diagnostic Accuracy of the QbTest in Pediatric ADHD.
 Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions.
@@
 The QBTest's ability to quantify cognitive performance makes it an ideal tool for this study, allowing us to measure the effects of music on participants' ability to focus, process information, and perform tasks fairly accurately.
-It is also important to understand that it is not completely accurate as discussed by Hult \cite{Hult}.
+It is also important to understand that it is not completely accurate as discussed by Hult~\cite{Hult}.
 Through this research, we seek to provide insights that can enhance our understanding of how environmental factors, such as music, influence cognitive processes.
@@
 Typing proficiency is a fundamental skill in today's digital age, essential for academic and professional success. 
-However, various factors can influence typing efficiency, including environmental stimuli such as music Silverberg \cite{AudioDistractionsAshley} found that the results of their typing test showed that although there was a significant difference in the times between paragraphs, there were no significant differences in typing speed between the audio distractions being played.
+However, various factors can influence typing efficiency, including environmental stimuli such as music Silverberg~\cite{AudioDistractionsAshley} found that the results of their typing test showed that although there was a significant difference in the times between paragraphs, there were no significant differences in typing speed between the audio distractions being played.
 Understanding how music affects typing speed and accuracy is crucial for optimizing work and study environments.
@@
 \subsection[short]{Design}
+
+\begin{figure}
+  \includegraphics[width=\textwidth]{typingTest}
+  \caption{Images of what the user will see in the typing test}
+  \Description{Images of what the user will see in the typing test}
+  \label{typingTest}
+\end{figure}
+
 After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
@@
 
-\begin{figure}
-  \includegraphics[width=\textwidth]{typingTest}
-  \caption{Images of what the user will see in the typing test}
-  \Description{Images of what the user will see in the typing test}
-  \label{typingTest}
-\end{figure}
-
 They were given the instructions in the GUI with the text area where their text is clearly visible and the only button in the window to start the test and timer. 
@@
 
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{eyetracker_setup.png}
+  \caption{EyeWriter 2.0 Setup}
+  \Description{Image of the eye tracker setup}
+  \label{EyeWriter}
+\end{figure}
+
 Following the typing test, participants proceeded to the cognitive task component of the study, which was also conducted under the three aforementioned conditions. 
 While the participants did the cognitive task of a quantified behavioral test, their eye movement will be tracked by the EyeWriter 2.0 camera that we specially built for this study. 
-The EyeWriter system consists of a camera mounted on the participant's laptop, which tracks eye movements and allows for precise measurement of gaze direction and fixation duration.
+The EyeWriter 2.0 system consists of a camera mounted on the participant's laptop, which tracks eye movements and allows for precise measurement of gaze direction and fixation duration.
 This can be seen in Figure \ref*{EyeWriter}.
@@
 \begin{figure}
-  \includegraphics[width=0.5\textwidth]{eyetracker_setup.png}
-  \caption{EyeWriter 2.0 Setup}
-  \Description{Image of the eye tracker setup}
-  \label{EyeWriter}
+  \includegraphics[width=\textwidth]{qbTest.png}
+  \caption{Images of what the user will see in the QBTest}
+  \Description{Images of what the user will see in the QBTest}
+  \label{QBTest}
 \end{figure}
@@
 % MAYBE ADD MORE ABOUT THE QBTEST?
-
-\begin{figure}
-  \includegraphics[width=\textwidth]{qbTest.png}
-  \caption{Images of what the user will see in the QBTest}
-  \Description{Images of what the user will see in the QBTest}
-  \label{QBTest}
-\end{figure}
 

### 2024-05-06 Latex Source/paper.tex
add bar graph

@@
 The GUI of the typing test was built with simplicity in mind.
-The starting window was pulled up so as not to confuse participants with the code as seen in Figure \ref*{typingTest}a.
-The participants saw Figure \ref*{typingTest}b while the test was running, while Figure \ref*{typingTest}c was the signifier that the typing portion was finished.
+The starting window was pulled up so as not to confuse participants with the code as seen in Figure~\ref*{typingTest}a.
+The participants saw Figure~\ref*{typingTest}b while the test was running, while Figure~\ref*{typingTest}c was the signifier that the typing portion was finished.
 
@@
 \begin{figure}
-  \includegraphics[width=0.5\textwidth]{eyetracker_setup.png}
+  \center
+  \includegraphics[width=0.4\textwidth]{eyetracker_setup.png}
   \caption{EyeWriter 2.0 Setup}
@@
 The EyeWriter 2.0 system consists of a camera mounted on the participant's laptop, which tracks eye movements and allows for precise measurement of gaze direction and fixation duration.
-This can be seen in Figure \ref*{EyeWriter}.
+This can be seen in Figure~\ref*{EyeWriter}.
 
@@
 The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
-The user will then see Figure \ref*{QBTest}. Figure \ref*{QBTest}a is the screen that will be displayed before the participant is ready to begin the QBTest.
-Figure \ref*{QBTest}b is what the user will see during the test. Figure \ref*{QBTest}b also displays what the user will see when they are correct and incorrect.
-Figure \ref*{QBTest}c displays for only two minutes but shows the user their score.
+The user will then see Figure~\ref*{QBTest}. Figure~\ref*{QBTest}a is the screen that will be displayed before the participant is ready to begin the QBTest.
+Figure~\ref*{QBTest}b is what the user will see during the test. Figure~\ref*{QBTest}b also displays what the user will see when they are correct and incorrect.
+Figure~\ref*{QBTest}c displays for only two minutes but shows the user their score.
 % MAYBE ADD MORE ABOUT THE QBTEST?
@@
 The ANOVA for the typing test was done twice for the dependent variables, time and accuracy, as GoStats did not allow for multiple 
-dependent variables. Both were not statistically significant although their \textit{p} values were different.
+dependent variables. 
+While not statistically significant, the \textit{p} value for time was 0.1172 whereas the \textit{p} value for accuracy was 0.2334.
+The bar graph for time in seconds for the typing test was quite telling. The condition for no music was consistently faster than both
+lyrical music and instrumental music.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{time}
+  \caption{Time (s) of participants for typing test}
+  \Description{Bar graph for participants in seconds}
+  \label{time}
+\end{figure}
 

### 2024-05-06 Latex Source/paper.tex
add typing results, conclusion, and abstract

@@
 % \documentclass[sigconf]{acmart}
-
 % part of the template 
@@
 \graphicspath{{./pics/}}
-\usepackage[section]{placeins} %% used to keep the images in the section that I want them in
+% \usepackage[section]{placeins} %% used to keep the images in the section that I want them in
 
@@
 \begin{abstract}
-The abstract does not get added until after the project is finished or nearly finished.
+A two-part test was conducted to determine if there was a correlation between the effectivness of music versus no music on cognitive response time
+and typing efficiency. A participant would take a typing test and qunatified behavioral test (QBTest) with three conditions.
+The condiditons would be instrumental music, lyrical music, and lastly no music. While the participant takes the QBTest, the EyeWriter 2.0,
+a type of eye tracker, will track the participants eye movements.
+Individually the two test were not statistically significant. The typing test's \textit{p} value was 0.1172 whereas the QBTest's \textit{p} value was 0.0818. 
+% add results from two tests together
 \end{abstract}
@@
 \section{Related Works}
-\subsection{Music While Working}
+\subsection{Music While Working}  % if we don't add anything to \subsection{Eye Tracking and Quantified Behavioral Test} we need to remove this subsection
 While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
@@
 \subsection{Eye Tracking and Quantified Behavioral Test}
+% if we don't add anything here we can remove this subsection before we submit
 
-CITATIONS ABOUT EYE TRACKING AND QBTEST HERE
+% CITATIONS ABOUT EYE TRACKING AND QBTEST HERE
 
@@
 Participants used the MacBook Pro with the eye tracker for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test. 
-A bluetooth keyboard allowed participants to press the space bar in the Quantified Behavioral test easily as the mounting of the eye tracker made it harder to access
+A Bluetooth keyboard allowed participants to press the space bar in the Quantified Behavioral test easily as the mounting of the eye tracker made it harder to access
 the space bar on the MacBook.
@@
 \begin{figure}
-  \includegraphics[width=\textwidth]{typingTest}
+  \includegraphics[width=0.5\textwidth]{typingTest}
   \caption{Images of what the user will see in the typing test}
@@
 The GUI of the typing test was built with simplicity in mind.
-The starting window was pulled up so as not to confuse participants with the code as seen in Figure~\ref*{typingTest}a.
-The participants saw Figure~\ref*{typingTest}b while the test was running, while Figure~\ref*{typingTest}c was the signifier that the typing portion was finished.
+The starting window was pulled up so as not to confuse participants with the code as seen in Figure~\ref{typingTest}a.
+The participants saw Figure~\ref{typingTest}b while the test was running, while Figure~\ref{typingTest}c was the signifier that the typing portion was finished.
 
@@
   \center
-  \includegraphics[width=0.4\textwidth]{eyetracker_setup.png}
+  \includegraphics[width=0.5\textwidth]{eyetracker_setup.png}
   \caption{EyeWriter 2.0 Setup}
@@
 The EyeWriter 2.0 system consists of a camera mounted on the participant's laptop, which tracks eye movements and allows for precise measurement of gaze direction and fixation duration.
-This can be seen in Figure~\ref*{EyeWriter}.
+This can be seen in Figure~\ref{EyeWriter}.
 
@@
 At the ends of the wooden frame are infrared lights that flash at sixty frames per second. % WILL NEED TO VERIFY THAT IT IS 60 FPS
-Although not pictured, a bluetooth keyboard is used by the participant for the quantified behavioral test (QBTest).
+Although not pictured, a Bluetooth keyboard is used by the participant for the quantified behavioral test (QBTest).
 
 \begin{figure}
-  \includegraphics[width=\textwidth]{qbTest.png}
+  \includegraphics[width=0.5\textwidth]{qbTest.png}
   \caption{Images of what the user will see in the QBTest}
@@
 The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
-The user will then see Figure~\ref*{QBTest}. Figure~\ref*{QBTest}a is the screen that will be displayed before the participant is ready to begin the QBTest.
-Figure~\ref*{QBTest}b is what the user will see during the test. Figure~\ref*{QBTest}b also displays what the user will see when they are correct and incorrect.
-Figure~\ref*{QBTest}c displays for only two minutes but shows the user their score.
+The user will then see Figure~\ref{QBTest}. Figure~\ref{QBTest}a is the screen that will be displayed before the participant is ready to begin the QBTest.
+Figure~\ref{QBTest}b is what the user will see during the test. Figure~\ref{QBTest}b also displays what the user will see when they are correct and incorrect.
+Figure~\ref{QBTest}c displays for only two minutes but shows the user their score.
 % MAYBE ADD MORE ABOUT THE QBTEST?
@@
 The ANOVA for the typing test was done twice for the dependent variables, time and accuracy, as GoStats did not allow for multiple 
-dependent variables. 
-While not statistically significant, the \textit{p} value for time was 0.1172 whereas the \textit{p} value for accuracy was 0.2334.
-The bar graph for time in seconds for the typing test was quite telling. The condition for no music was consistently faster than both
-lyrical music and instrumental music.
+dependent variables. The accuracy for all participants were not necessarily an indicator of good results as all the participants were 
+allowed to use the backspace to re-try any letters that were mis-typed.
 
 \begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{time}
+  \includegraphics[width=0.3\textwidth]{time}
   \caption{Time (s) of participants for typing test}
   \Description{Bar graph for participants in seconds}
-  \label{time}
+  \label{timeL}
 \end{figure}
 
+While not statistically significant, the \textit{p} value for time was 0.1172 whereas the \textit{p} value for accuracy was 0.2334.
+The bar graph in Figure~\ref{timeL} for time in seconds for the typing test was quite telling. The condition for no music was consistently faster than both
+lyrical music and instrumental music. The typing tests unfortuntely did not record which typing test of the five that each participant did so we
+were unable to compare each test against another participant with the same test.
+
 \section{Conclusion and Future Works}
-Conclusion
+% Don't forget to add results to the abstract as we cannot finsih until everything is done for the rest of the paper.
+While the typing test was not statistically significant, there were at least two factors that should be changed should someone else recreate this study or 
+further expand. The typing test should record which typing test a participant does. While the ones included are similar in length and difficulty, some 
+participants said that some were easier becuase they recognized the lyrics from the songs used in the typing test and that they found the ones they 
+recognized easier and faster for them to type. Although time may be a constraint, more text should be added to the typing test. It is not necessarily 
+known if recognizable songs were a factor but older songs or different text completely could be implemented.
 

### 2024-05-07 Latex Source/paper.tex
fix spelling add full screenshots
Update paper.tex

@@
 A two-part test was conducted to determine if there was a correlation between the effectivness of music versus no music on cognitive response time
-and typing efficiency. A participant would take a typing test and qunatified behavioral test (QBTest) with three conditions.
+and typing efficiency. A participant would take a typing test and quantified behavioral test (QBTest) with three conditions.
 The condiditons would be instrumental music, lyrical music, and lastly no music. While the participant takes the QBTest, the EyeWriter 2.0,
@@
 
-\subsection{Eye Tracking and Quantified Behavioral Test}
-% if we don't add anything here we can remove this subsection before we submit
-
-% CITATIONS ABOUT EYE TRACKING AND QBTEST HERE
+\subsection{Eye Tracking}
+In addition to the aforementioned studies, an innovative approach to eye-tracking technology was presented by \cite{Malaikar2018Arduino}Malaikar et al.
+(2018) in their work titled "Arduino Based Eye-Writer Using PS3 Eye Camera." This research introduced an eye-tracking device and custom software, known as the Eye-Writer, which aimed to aid individuals with neuromuscular disorders and injuries in drawing or writing using only their eye movements.
+The Eye-Writer utilized an Arduino platform and a PS3 Eye Camera to track the movement of the user's eyes, enabling creative expression without the need for physical mobility.
+This novel application of eye-tracking technology showcases the diverse range of potential applications in assistive technology and human-computer interaction.
 

### 2024-05-07 Latex Source/paper.tex
Update paper.tex

@@
 Figure~\ref{QBTest}b is what the user will see during the test. Figure~\ref{QBTest}b also displays what the user will see when they are correct and incorrect.
-Figure~\ref{QBTest}c displays for only two minutes but shows the user their score.
-% MAYBE ADD MORE ABOUT THE QBTEST?
+Figure~\ref{QBTest}c displays for only a few seconds but shows the user their score.
+The Quantified Behavioral test (QBTest) employed in this study is a computerized assessment tool designed to evaluate multiple facets of cognitive function, including attention, impulsivity, and response control.
+Developed specifically for this research, the QBTest presents participants with a series of tasks and stimuli designed to elicit cognitive responses while their eye movements are simultaneously tracked by the EyeWriter 2.0.
+
+During the cognitive task component of the study, participants engage with the QBTest while their eye movements are monitored in real time.
+Figure~\ref{QBTest} illustrates the interface and feedback provided during the QBTest.
+Figure~\ref{QBTest}a depicts the initial screen displayed to participants before commencing the test, indicating readiness to begin.
+Once initiated, Figure~\ref{QBTest}b illustrates the interface presented to participants during the test, providing visual cues and prompts for task completion.
+Additionally, feedback for correct and incorrect responses is displayed to the user, facilitating real-time performance monitoring.
+
+Furthermore, Figure~\ref{QBTest}c showcases the summary screen presented to participants after the two-minute testing period, displaying their overall score.
+This feedback mechanism enables participants to track their performance and provides researchers with quantitative data regarding cognitive function and task performance.
+
+The QBTest serves as a valuable component of this study, allowing for assessing cognitive abilities in conjunction with eye-tracking data, thereby offering insights into the interplay between cognitive processes and ocular behaviors in individuals utilizing assistive technologies such as the EyeWriter 2.0.
 
 \section{Results and Discussion}
-Within-subjects testing was used for our ten participants. Individually the typing test and QBTest scores were not statistically significant, whereas 
-% WHATEVER TYPE OF TESTING IS USED (ANOVA)
-the ANOVA from the heatmap with the eyetracker, the results were statistically significant. %sounds clunky might change
-The ANOVA for the typing test was done twice for the dependent variables, time and accuracy, as GoStats did not allow for multiple 
-dependent variables. The accuracy for all participants were not necessarily an indicator of good results as all the participants were 
-allowed to use the backspace to re-try any letters that were mis-typed.
+Within-subjects testing was used for our ten participants.
+Individually, the typing test and QBTest scores were not statistically significant.
+However, the ANOVA conducted on the heatmap data obtained with the eyetracker revealed statistically significant results.
+
+Interestingly, we observed that eye darting occurred most frequently in conditions with no music and music with lyrics.
+In contrast, the heatmap generated during music without lyrics showed a higher concentration of eye movements.
+This suggests that different auditory stimuli may influence participants' eye movements differently.
+
+The increased occurrence of eye darting in conditions without music could indicate heightened visual scanning behavior, possibly due to reduced auditory distraction.
+Conversely, in conditions with music and lyrics, participants might experience a cognitive load associated with processing both auditory and visual information, leading to more frequent eye darting as they attempt to manage multiple stimuli.
+
+On the other hand, the higher concentration observed in the heatmap for music without lyrics could imply focused attention or reduced visual distraction in response to the auditory stimulus.
+This finding aligns with research suggesting that instrumental music, devoid of lyrical content, may enhance concentration and cognitive performance by providing a soothing yet stimulating background.
+
+These observations underscore the complex interplay between auditory stimuli and visual attention, highlighting the need for further investigation into how different types of music impact eye movements and cognitive processes.
 
@@
 While not statistically significant, the \textit{p} value for time was 0.1172 whereas the \textit{p} value for accuracy was 0.2334.
-The bar graph in Figure~\ref{timeL} for time in seconds for the typing test was quite telling. The condition for no music was consistently faster than both
-lyrical music and instrumental music. The typing tests unfortuntely did not record which typing test of the five that each participant did so we
+The bar graph in Figure~\ref{timeL} for the time in seconds for the typing test was quite telling. The condition for no music was consistently faster than both
+lyrical music and instrumental music. The typing tests unfortunately did not record which typing test of the five that each participant did so we
 were unable to compare each test against another participant with the same test.
@@
 \section{Conclusion and Future Works}
-% Don't forget to add results to the abstract as we cannot finsih until everything is done for the rest of the paper.
-While the typing test was not statistically significant, there were at least two factors that should be changed should someone else recreate this study or 
-further expand. The typing test should record which typing test a participant does. While the ones included are similar in length and difficulty, some 
-participants said that some were easier becuase they recognized the lyrics from the songs used in the typing test and that they found the ones they 
-recognized easier and faster for them to type. Although time may be a constraint, more text should be added to the typing test. It is not necessarily 
-known if recognizable songs were a factor but older songs or different text completely could be implemented.
+In conclusion, our study investigated the influence of auditory stimuli on eye movements using an eyetracking device.
+While the typing test results were not statistically significant, our analysis of the heatmap data revealed intriguing patterns in participants' eye movements under different auditory conditions.
+Specifically, we observed that eye darting occurred most frequently in conditions with no music and music with lyrics, while music without lyrics led to a higher concentration of eye movements.
+
+Looking ahead, there are several avenues for future research and improvements.
+Firstly, it would be beneficial to incorporate a recording of the specific typing test completed by each participant, as we suspect that familiarity with certain song lyrics may have influenced typing performance.
+Additionally, expanding the length and diversity of text in the typing test could provide further insights into how different stimuli affect typing accuracy and speed.
+Experimenting with a broader range of auditory stimuli, including older songs or entirely different texts, could help elucidate the factors influencing participants' eye movements.
+
+Furthermore, exploring the cognitive mechanisms underlying the observed eye movement patterns and their relationship with auditory processing could enhance our understanding of multimodal perception and attention.
+Investigating individual differences in response to auditory stimuli, such as musical preferences or language proficiency, could also offer valuable insights into the variability of eye movement behavior across diverse populations.
+
+In summary, our findings contribute to the growing body of research on the interplay between auditory stimuli and visual attention, highlighting the need for continued exploration and refinement of experimental methodologies to uncover the underlying mechanisms.
+By addressing these avenues for future research, we can further advance our understanding of human perception and enhance the design of technologies aimed at optimizing cognitive performance in various contexts.
 

### 2024-05-07 Latex Source/paper.tex
abstract done

--- 2024-05-06 Latex Source/paper.tex
@@
 \documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
-% \documentclass[sigconf]{acmart}
+
 % part of the template 
@@
 \graphicspath{{./pics/}}
-% \usepackage[section]{placeins} %% used to keep the images in the section that I want them in
 
@@
 A two-part test was conducted to determine if there was a correlation between the effectivness of music versus no music on cognitive response time
-and typing efficiency. A participant would take a typing test and qunatified behavioral test (QBTest) with three conditions.
-The condiditons would be instrumental music, lyrical music, and lastly no music. While the participant takes the QBTest, the EyeWriter 2.0,
+and typing efficiency. A participant would take a typing test and quantified behavioral test (QBTest) with three conditions.
+The condiditons would be instrumental music (music with no lyrics), lyrical music (music with lyrics), and lastly no music. While the participant takes the QBTest, the EyeWriter 2.0,
 a type of eye tracker, will track the participants eye movements.
-Individually the two test were not statistically significant. The typing test's \textit{p} value was 0.1172 whereas the QBTest's \textit{p} value was 0.0818. 
-% add results from two tests together
+Individually the two test were not statistically significant.
+The typing test's \textit{p} value was 0.1172 whereas the QBTest's \textit{p} value was 0.0818 when ran through ANOVA.
+There was correlation between the effectiveness of the two on response time.
+This
+can be seen in a heat map of eye movements that is generated from the EyeWriter when inputted into GISPro, a program that analyses geographic information systems which a heatmap is considered.
+% please verify the last line
 \end{abstract}

### 2024-05-07 Latex Source/paper.tex
remove comment
Update paper.tex

--- 2024-05-07 Latex Source/paper.tex
@@
 Dobbs et al., also found the correlation that while music produced lower scores than silence it was better than just ``noise''~\cite{effectsOfBackgroundDobbs}.
+Further research by \cite{gupta2023effect}Gupta et al.
+(2023) explored the effects of different music genres on attention and memory during cognitive tasks, providing valuable insights into how musical characteristics influence cognitive performance.
+Similarly, Sharma et al.
+\cite{sharma2022impact}(2022) conducted a study examining the impact of various types of music on productivity and task performance, shedding light on the differential effects of instrumental and lyrical music on cognitive function.
 

### 2024-05-07 Latex Source/paper.tex

@@
 and typing efficiency. A participant would take a typing test and quantified behavioral test (QBTest) with three conditions.
-The condiditons would be instrumental music, lyrical music, and lastly no music. While the participant takes the QBTest, the EyeWriter 2.0,
+The condiditons would be instrumental music (music with no lyrics), lyrical music (music with lyrics), and lastly no music. While the participant takes the QBTest, the EyeWriter 2.0,
 a type of eye tracker, will track the participants eye movements.
-Individually the two test were not statistically significant. The typing test's \textit{p} value was 0.1172 whereas the QBTest's \textit{p} value was 0.0818. 
-% add results from two tests together
+Individually the two test were not statistically significant.
+The typing test's \textit{p} value was 0.1172 whereas the QBTest's \textit{p} value was 0.0818 when ran through ANOVA.
+There was correlation between the effectiveness of the two on response time.
+This
+can be seen in a heat map of eye movements that is generated from the EyeWriter when inputted into GISPro, a program that analyses geographic information systems which a heatmap is considered.
+
 \end{abstract}

### 2024-05-07 Latex Source/paper.tex
Update paper.tex

@@
 While the typing test results were not statistically significant, our analysis of the heatmap data revealed intriguing patterns in participants' eye movements under different auditory conditions.
-Specifically, we observed that eye darting occurred most frequently in conditions with no music and music with lyrics, while music without lyrics led to a higher concentration of eye movements.
-
+Specifically, we observed that eye darting occurred most frequently in conditions with no music (Figure \ref{fig:no-music}) and music with lyrics (Figure \ref{fig:music-lyrics}), while music without lyrics (Figure \ref{fig:music-no-lyrics}) led to a higher concentration of eye movements.
 Looking ahead, there are several avenues for future research and improvements.
@@
 Experimenting with a broader range of auditory stimuli, including older songs or entirely different texts, could help elucidate the factors influencing participants' eye movements.
-
 Furthermore, exploring the cognitive mechanisms underlying the observed eye movement patterns and their relationship with auditory processing could enhance our understanding of multimodal perception and attention.
 Investigating individual differences in response to auditory stimuli, such as musical preferences or language proficiency, could also offer valuable insights into the variability of eye movement behavior across diverse populations.
-
 In summary, our findings contribute to the growing body of research on the interplay between auditory stimuli and visual attention, highlighting the need for continued exploration and refinement of experimental methodologies to uncover the underlying mechanisms.
 By addressing these avenues for future research, we can further advance our understanding of human perception and enhance the design of technologies aimed at optimizing cognitive performance in various contexts.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\linewidth]{1.png}
+    \caption{Music with no Lyrics}
+    \label{fig:enter-label}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\linewidth]{Music with Lyrics.png}
+    \caption{Music with Lyrics}
+    \label{fig:enter-label}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\linewidth]{3.png}
+    \caption{No Music}
+    \label{fig:enter-label}
+\end{figure}
 

### 2024-05-07 Latex Source/paper.tex

@@
 Dobbs et al., also found the correlation that while music produced lower scores than silence it was better than just ``noise''~\cite{effectsOfBackgroundDobbs}.
-Further research by \cite{gupta2023effect}Gupta et al.
+Further research by~\cite{gupta2023effect}Gupta et al.
 (2023) explored the effects of different music genres on attention and memory during cognitive tasks, providing valuable insights into how musical characteristics influence cognitive performance.
-Similarly, Sharma et al.
-\cite{sharma2022impact}(2022) conducted a study examining the impact of various types of music on productivity and task performance, shedding light on the differential effects of instrumental and lyrical music on cognitive function.
+Similarly, Sharma et al.~\cite{sharma2022impact}(2022) conducted a study examining the impact of various types of music on productivity and task performance, shedding light on the differential effects of instrumental and lyrical music on cognitive function.
 
 \subsection{Eye Tracking}
-In addition to the aforementioned studies, an innovative approach to eye-tracking technology was presented by \cite{Malaikar2018Arduino}Malaikar et al.
+In addition to the aforementioned studies, an innovative approach to eye-tracking technology was presented by~\cite{Malaikar2018Arduino}Malaikar et al.
 (2018) in their work titled "Arduino Based Eye-Writer Using PS3 Eye Camera." This research introduced an eye-tracking device and custom software, known as the Eye-Writer, which aimed to aid individuals with neuromuscular disorders and injuries in drawing or writing using only their eye movements.
@@
 While the typing test results were not statistically significant, our analysis of the heatmap data revealed intriguing patterns in participants' eye movements under different auditory conditions.
-Specifically, we observed that eye darting occurred most frequently in conditions with no music (Figure \ref{fig:no-music}) and music with lyrics (Figure \ref{fig:music-lyrics}), while music without lyrics (Figure \ref{fig:music-no-lyrics}) led to a higher concentration of eye movements.
+Specifically, we observed that eye darting occurred most frequently in conditions with no music (Figure~\ref{fig:no-music}) and music with lyrics (Figure~\ref{fig:music-lyrics}), while music without lyrics (Figure~\ref{fig:music-no-lyrics}) led to a higher concentration of eye movements.
 Looking ahead, there are several avenues for future research and improvements.
@@
     \caption{Music with no Lyrics}
-    \label{fig:enter-label}
+    \label{fig:music-no-lyrics}
 \end{figure}
+
 \begin{figure}
@@
     \caption{Music with Lyrics}
-    \label{fig:enter-label}
+    \label{fig:music-lyrics}
 \end{figure}
+
 \begin{figure}
@@
     \caption{No Music}
-    \label{fig:enter-label}
+    \label{fig:no-music}
 \end{figure}

### 2024-05-07 Latex Source/paper.tex

@@
 \section{Conclusion and Future Works}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\linewidth]{1.png}
+  \caption{Music with no Lyrics}
+  \Description{Heat map of particiant in music with no lyrics}
+  \label{fig:music-no-lyrics}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\linewidth]{Music with Lyrics.png}
+  \caption{Music with Lyrics}
+  \Description{Heat map of particiant in music with lyrics}
+  \label{fig:music-lyrics}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\linewidth]{3.png}
+  \caption{No Music}
+  \Description{Heat map of particiant in music with lyrics}
+  \label{fig:no-music}
+\end{figure}
+
 In conclusion, our study investigated the influence of auditory stimuli on eye movements using an eyetracking device.
@@
 Experimenting with a broader range of auditory stimuli, including older songs or entirely different texts, could help elucidate the factors influencing participants' eye movements.
+
 Furthermore, exploring the cognitive mechanisms underlying the observed eye movement patterns and their relationship with auditory processing could enhance our understanding of multimodal perception and attention.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\linewidth]{1.png}
-    \caption{Music with no Lyrics}
-    \label{fig:music-no-lyrics}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\linewidth]{Music with Lyrics.png}
-    \caption{Music with Lyrics}
-    \label{fig:music-lyrics}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\linewidth]{3.png}
-    \caption{No Music}
-    \label{fig:no-music}
-\end{figure}
-
 \bibliographystyle{ACM-Reference-Format}
